\documentclass[oneside, 11pt]{amsart}

\usepackage{amsmath, mathtools, amssymb, amsthm, amscd, alltt, graphicx, comment}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[breaklinks=false,unicode]{hyperref}
\usepackage[capitalise]{cleveref}
\usepackage[matrix,arrow,curve]{xy}
\usepackage[notref, notcite]{showkeys}

\usepackage[backend=biber, bibencoding=utf8, giveninits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
\addbibresource{f4paper.bib}
\renewbibmacro*{volume+number+eid}{\ifentrytype{article}{\- \iffieldundef{volume}{}{Vol.~\printfield{volume},}\iffieldundef{number}{}{ No.~\printfield{number},}}}
\renewbibmacro{in:}{\ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}
\newbibmacro{string+doi}[1]{\iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{https://dx.doi.org/\thefield{doi}}{#1}}}
\DeclareFieldFormat[article, inproceedings, inbook, book, online]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
\renewcommand*{\bibfont}{\footnotesize}

\numberwithin{equation}{section}

\newtheorem{lemma}{Lemma} \numberwithin{lemma}{section}
\newtheorem{prop}[lemma]{Proposition}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[lemma]{Corollary} 
\newtheorem*{theorem*}{Theorem} 

\theoremstyle{definition} 
\newtheorem{df}[lemma]{Definition} \Crefname{df}{Definition}{Definitions}
\newtheorem{example}[lemma]{Example} \Crefname{example}{Example}{Examples}

\theoremstyle{remark} 
\newtheorem{rem}[lemma]{Remark}
\newtheorem{conv}[lemma]{Convention} \Crefname{conv}{Convention}{Conventions}

\DeclareMathOperator\St{St}
\DeclareMathOperator\Ker{Ker}
\DeclareMathOperator\GG{G}
\DeclareMathOperator\E{E}
\DeclareMathOperator\Torus{T}
\DeclareMathOperator{\Pro}{Pro}
\DeclareMathOperator\Aut{Aut}


\newcommand{\Set}{\mathbf{Set}}
\newcommand{\Group}{\mathbf{Grp}}
\newcommand{\Rng}{\mathbf{Rng}}
\newcommand{\Fun}{\mathbf{Fun}}
\newcommand{\Mod}{\mathbf{Mod}}
\newcommand{\op}{\mathrm{op}}
\newcommand{\ZZ}{\mathbb{Z}}

\newcommand{\otimeshat}{\mathbin{\widehat{\otimes}}}

\newcommand{\up}[2]{{^{#1}\!{#2}}}

\newcommand{\rA}{\mathsf{A}}
\newcommand{\rB}{\mathsf{B}}
\newcommand{\rC}{\mathsf{C}}
\newcommand{\rD}{\mathsf{D}}
\newcommand{\rE}{\mathsf{E}}
\newcommand{\rF}{\mathsf{F}}
\newcommand{\rG}{\mathsf{G}}

\title{Centrality of $K_2$ for Chevalley groups}
\keywords {Steinberg group, pro-group, Suslin normality theorem. {\em Mathematical Subject Classification (2010):} 19C09, 20G35, 20H05}

\author {Andrei Lavrenov} \email{avlavrenov at gmail.com}
\author {Sergey Sinchuk} \email {sinchukss at gmail.com}
\author {Egor Voronestky} \email {voronetckiiegor at yandex.ru}

\date {\today}

\begin{document}
\maketitle

\section{Introduction}
This paper is the final installment in the series of articles by the third-named author devoted to the proof of centrality of $\mathrm K_2$ modeled on linear groups. In the previous articles of the series~\cite{Vor1, Vor2} the third-named author has already proven the centrality of $\mathrm K_2$ for the so-called {\it odd unitary groups}. These groups, introduced by V.~Petrov in~\cite{Pe05}, encompass a large class of classical-like groups over noncommutative rings including, in particular, the usual classical Chevalley groups.

Let us briefly explain the reader how our result fit into the general picture.
Recall that Steinberg groups $\St(\Phi, R)$ are certain groups given by generators and relations, that were classically introduced by R.~Steinberg and J.~Milnor in~\cite{St62, Milnor} as combinatorial approximations of the simply-connected Chevalley groups. For example, every element of the special linear group $\mathrm{SL}_n(\mathbb F_q)$ over a finite field can be presented as a product of elementary transvections $t_{ij}(a)$ ($i\neq j$, $a\in \mathbb F_q$). These elements are taken as the generators of the Steinberg group $\St_n(\mathbb{F}_q)$. 
Moreover, any two such presentations of the same element of $\mathrm{SL}_n(\mathbb{F}_q)$ can be related one with the other
 by a sequence of the following ``elementary'' transformations: 
\begin{itemize} 
 \item $t_{ij}(a)t_{ij}(b) = t_{ij}(a+b)$; 
 \item $t_{ij}(a)t_{hk}(b) = t_{hk}(b)t_{ij}(a)$ for $j\neq h$ and $i\neq k$; 
 \item $t_{ij}(a)t_{jk}(b)t_{ij}(-a)t_{jk}(-b) = t_{ik}(ab)$ for $i\neq k$.
\end{itemize} 
These transformations are taken as the defining relations of the Steinberg group $\St_n(\mathbb{F}_q)$.
Thus, in the finite field case one has $\St_n(\mathbb{F}_q) \cong \mathrm{SL}_n(\mathbb{F}_q)$.

For an infinite field $F$ the Steinberg group $\mathrm{St}(\Phi,\,F)$ no longer coincides with the simply-connected Chevalley group $\GG_{sc}(\Phi, R)$, but rather is the universal central extension of the latter.
By the classical theory of central extensions the kernel of the natural homomorphism $\St(\Phi,\,F)\to\GG_{sc}(\Phi, F)$ coincides with the Schur multiplier $\mathrm H_2(\mathrm G_{\mathrm{sc}}(\Phi,\,F),\,\mathbb Z)$. The concrete presentation of this group in the field case was obtained by H.~Matsumoto in~\cite{Ma69}. Similar presentation for the special linear group over a skew field also has been obtained by U.~Rehmann in~\cite{Re78}.

J.~Milnor has shown that the linear Steinberg group $\St_n(R)$ over a general ring has trivial Schur multiplier provided $n \geq 4$.
This shows that $\St_n(R)$ is a good candidate for the role of the universal central extension of its image in $\GG_{sc}(\Phi, R)$. 
The centrality of the homomorphism $\St_n(R) \to \mathrm{GL}_n(R)$ for finite $n$ was not studied by Milnor as he was more concerned with the case $n = \infty$. Recall that the functor $\mathrm K_2$ was originally defined by Milnor as the kernel of the homomorphism $\St_\infty(R) \to \mathrm{GL}_\infty(R)$, i.\,e. as the group of ``non-elementary'' relations between transvections of the infinite-dimensional general linear group.
Milnor's approach was followed by M.~Stein who defined Steinberg groups $\St(\Phi, R)$ in the context of arbitrary Chevalley groups and, by analogy,  defined the functor $\mathrm K_2(\Phi, R)$ as the kernel of the natural homomorphism $\mathrm{st}\colon \St(\Phi, R) \to \GG_{sc}(\Phi, R)$;  see~\cref{def:Steinberg}. Also M.~Stein together with W.~van der Kallen were able to compute Schur multipliers of $\St(\Phi, R)$ for $\Phi$ of rank $\geq 3$; see~\cite{St71, vdKStein}. The triviality of Schur multipliers for unitary Steinberg groups of sufficiently large rank in the noncommutative case has also been studied in~\cite{Bak, Tang, LavU, LavOU}.

\subsection{Acknowledgements}
The work of the second-named author was supported by RFBR grant No 18-31-20044.

\section{Preliminaries}
Throughout this paper all commutators are left normed, i.\,e. $[x, y] = xyx^{-1}y^{-1}$. We denote by $x^y$ and $\up{y}x$ the elements $xyx^{-1}$ and $yxy^{-1}$.
In this paper we also make use the following commutator identities:
\begin{align}
\label{eq:comm-mult-rhs}[x,\ yz]& =   [x,\ y] \cdot \up{y}[x,\ z],
\\ \label{eq:comm-mult-lhs}[xy,\ z]& = \up{x}[y,\ z] \cdot [x,\ z],
\end{align}
\begin{equation} \label{eq:HW-corr} [x,z] = 1 \text{ implies } [x, [y,z]] = [[x,y],\up{y}z].
\end{equation}


\subsection{Generalities on pro-objects}
Let \(\mathcal C\) be an arbitrary category.
In this section we recall the construction of the pro-completion of \(\mathcal C\) (cf. \cite[Section~6.1]{SK06}).

Recall that a nonempty small category \(\mathcal I\) is called {\it filtered} if
\begin{itemize}
 \item for any two objects \(i, k \in Ob(\mathcal{I})\) there is a diagram \(i \to j \leftarrow k\) in \(\mathcal I\) (i.\,e. $i$ and $k$ have an upper bound);
 \item every two parallel morphisms \(i \rightrightarrows j\) are equalized by some morphism \(j \to k\) in \(\mathcal I\).
\end{itemize}
A {\it pro-object} in \(\mathcal C\) is, by definition, a functor $X^{(\infty)}\colon \mathcal{I}_X^{\op} \to \mathcal{C}$, i.\,e. a contravariant functor from a filtered category \(\mathcal I_X\), called {\it the category of indices of $X^{(\infty)}$}, to the category \(\mathcal C\). 

We denote by \(X^{(i)}\) the value of \(X^{(\infty)}\) on an index \(i\).
The values of the functor $X^{(\infty)}$ on the arrows of $\mathcal{I}$ are called the {\it structure morphisms} of $X^{(\infty)}$.

The category of pro-objects is denoted by \(\Pro(\mathcal C)\). The hom-sets in this category are given by the formula
\begin{equation} \label{eq:pro-c-hom} \Pro(\mathcal C)(X^{(\infty)}, Y^{(\infty)}) = \varprojlim_{j \in \mathcal I_Y} \varinjlim_{i \in \mathcal I_X} \mathcal C(X^{(i)}, Y^{(j)}). \end{equation}
Let us recall a more explicit description of morphisms in \(\Pro(\mathcal C)\). 
By definition, a {\it pre-morphism} \(f \colon X^{(\infty)} \to Y^{(\infty)}\) consists of the following data:
\begin{itemize}
\item a set-theoretic function \(f^* \colon Ob(\mathcal{I_Y}) \to Ob(\mathcal{I_X})\);
\item a collection of morphisms \(f^{(i)} \colon X^{(f^*(i))} \to Y^{(i)}\) in $\mathcal{C}$ parametrized by $i \in Ob(\mathcal{I_Y})$. These morphisms are required to satisfy the following additional assumption: for every morphism \(i \to j\) in \(\mathcal I_Y\) there exists a sufficiently large index \(k \in Ob(\mathcal{I_X})\) such that the composite morphisms \(X^{(k)} \to X^{(f^*(i))} \to Y^{(i)}\) and \(X^{(k)} \to X^{(f^*(j))} \to Y^{(j)} \to Y^{(i)}\) are equal. \end{itemize}
The composition of two pre-morphisms \(f \colon X^{(\infty)} \to Y^{(\infty)}\) and \(g \colon Y^{(\infty)} \to Z^{(\infty)}\) is defined as the pre-morphism \(g \circ f\), where \((g \circ f)^*(i) = f^*(g^*(i))\) and \((g \circ f)^{(i)} = g^{(i)} \circ f^{(g^*(i))}\).

Two parallel pre-morphisms \(f, g \colon X^{(\infty)} \to Y^{(\infty)}\) are called equivalent if for every \(i \in Ob(\mathcal I_Y)\) there exists a sufficiently large index \(j \in Ob(\mathcal I_X)\) such that the composite morphisms \(X^{(j)} \to X^{(f^*(i))} \to Y^{(i)}\) and \(X^{(j)} \to X^{(g^*(i))} \to Y^{(i)}\) are equal. Finally, a {\it morphism} \(X^{(\infty)} \to Y^{(\infty)}\) is an equivalence class of pre-morphisms. Note that the equivalence relation is preserved by the composition operation.

There is a fully faithful functor $\mathcal{C} \to \Pro(\mathcal{C})$ sending \(X \in Ob(\mathcal C)\) to the pro-object $X \colon \mathbf{1}^\op \to \mathcal{C}$. It is clear from~\eqref{eq:pro-c-hom}  that
\begin{align}
 \Pro(\mathcal C)(X, Y) &\cong \mathcal C(X, Y);\\
 \Pro(\mathcal C)(X^{(\infty)}, Y) &\cong \varinjlim_{i \in \mathcal I_X} \mathcal C(X^{(i)}, Y); \label{eq:pro-c-hom-2}\\
 \Pro(\mathcal C)(X, Y^{(\infty)}) &\cong \varprojlim_{i \in \mathcal I_Y} \mathcal C(X, Y^{(i)}).
\end{align}

Moreover, it is also clear from~\eqref{eq:pro-c-hom} and~\eqref{eq:pro-c-hom-2} that the following assertion holds.
\begin{lemma} \label{lem:proobj-is-a-limit}
  \(X^{(\infty)}\) is the projective limit of \(X^{(i)}\) in the category \(\Pro(\mathcal C).\)
\end{lemma}

The category of pro-sets \(\Pro(\Set)\) has all finite limits by \cite[Prop.~6.1.18]{SK06} and therefore is a cartesian monoidal category.

Let us describe an explicit construction of limits in one important special case. Let $X^{(\infty)}, Y^{(\infty)} \colon \mathcal{I}^\op \to \Set\) be a pair of pro-sets with the same index category. Recall that the pointwise product of functors $X^{(\infty)} \times Y^{(\infty)} \colon \mathcal{I}^\op \to \Set$ is given by $(X^{(\infty)} \times Y^{(\infty)})^{(i)} = X^{(i)} \times Y^{(i)}$. Clearly, $X^{(\infty)} \times Y^{(\infty)}$ is a product of $X^{(\infty)}$ and $Y^{(\infty)}$  in the category $\Fun(\mathcal{I}^\op, \Set)$. 

There is an obvious identity-on-objects functor $\Fun(\mathcal{I}^\op, \Set) \to \Pro(\Set)$ sending a natural transformation $\varphi \colon X^{(\infty)} \to Y^{(\infty)}$ to the morphism of pro-sets given by the pre-morphism $\varphi^* = \mathrm{id}_{Ob(\mathcal{I})}$, $\varphi^{(i)} = \varphi_i$. The diagonal morphism $\Delta \colon X^{(\infty)} \to X^{(\infty)} \times X^{(\infty)}$ and the canonical projection morphisms \(\pi_X\colon X^{(\infty)} \times Y^{(\infty)} \to X^{(\infty)}, \pi_Y\colon X^{(\infty)} \times Y^{(\infty)} \to Y^{(\infty)}\) can be defined in the category $\Pro(\Set)$ as the images of the corresponding natural transformations in $\Fun(\mathcal{I}^\op, \Set)$ under this functor.

We claim that the point-wise product $X^{(\infty)} \times Y^{(\infty)}$ satisfies the universal property of products in the category $\Pro(\Set)$. Indeed, this follows from~\eqref{eq:pro-c-hom} and the fact that filtered colimits commute with finite limits. This argument also shows that arbitrary finite limits of pro-sets with the same index category can be computed pointwise.

\subsection{Group and ring objects in pro-sets}
In this paper we consider only commutative rings.
To distinguish between unital and non-unital rings we reserve the word ``ring'' only for unital rings and refer to non-unital rings as {\it rngs}.
We denote the category of rings (resp. rngs) as $\textbf{Ring}$ (resp. $\textbf{Rng}$).

Let $T$ be an algebraic theory. Throughout this paper we will be mostly interested in the case when $T$ is the theory of groups or the theory of rngs.

Since the category $\Pro(\Set)$ is cartesian monoidal, we may speak of the category $\Mod(T, \Pro(\Set))$ of models of $T$ in \(\Pro(\Set)\).
In the special case when $T$ is the theory of groups (resp. rngs) this category is precisely the category of group (resp. rng) objects in $\Pro(\Set)$.

The category of pro-groups \(\Pro(\Group)\) embeds into \(\Pro(\Set)\). Every pro-group is a group object in \(\Pro(\Set)\). It is easy to see that a morphism \(f \in \Pro(\Set)(G^{(\infty)}, H^{(\infty)})\) between pro-groups comes from \(\Pro(\Group)\) if and only if it is a morphism of group objects. Thus, $\Pro(\Group)$ is a full subcategory of the category of group objects in $\Pro(\Set)$.

\begin{df} \label{df-pro-set-morphisms} 
 Let $n$ be a natural number and $F_{n, T}$ be the free algebra on $n$ generators in the theory $T$.
 If $T$ is the theory of groups, then $F_n$ is the free group $F(t_1,\ldots, t_n)$.
 Similarly, if $T$ is the theory of rngs, $F_{n, T}$ is the sub-rng of the ring $\mathbb{Z}[t_1,\ldots, t_n]$ consisting of polynomials over $\mathbb{Z}$ without free terms.
 
 Given a word $w \in F_{n, T}$ and a $T$-model $X^{(\infty)}$ in $\Pro(\Set)$, one can construct the $\Pro(\Set)$-morphism
 \[ w^{(\infty)} \colon \underbrace{X^{(\infty)} \times \ldots \times X^{(\infty)}}_{n\text{ times}} \to X^{(\infty)}, \]
 which ``interprets'' the word $w$. This morphism can be obtained as an appropriate composition of diagonal morphisms $\Delta_{X^{(\infty)}}$, projections $\pi_i$ 
 (which are part of the structure of a cartesian monoidal category on $\Pro(\Set)$) 
 and the morphisms defining the structure of a $T$-model on $X^{(\infty)}$.
 
 In order to shorten the notation, to denote the interpretation morphism $w^{(\infty)}$ we often use the original term for $w$, in which every symbol of a free variable $t_i$ is replaced by the symbol $t_i^{(\infty)}$.
\end{df}

\begin{example}\label{example-commutator}
Consider the case when $T$ is the theory of groups.
Let $G^{(\infty)}$ be a group object in $\Pro(\Set)$ and $w = [t_1, t_2] = t_1 t_2 t_1^{-1} t_2^{-1} \in F(t_1, t_2)$ be the word representing the generic commutator.
In this case the interpretation morphism $w^{(\infty)}$ (also denoted $[t_1^{(\infty)}, t_2^{(\infty)}]$) can be defined as the composition
 \[ \xymatrix{G^{(\infty)} \times G^{(\infty)} \ar[r]^(.35){\Delta \times \Delta} & G^{(\infty)} \times G^{(\infty)} \times G^{(\infty)} \times G^{(\infty)} \ar[d]_{\langle \pi_1, \pi_3, i\pi_2, i\pi_4 \rangle} & \\
    & G^{(\infty)} \times G^{(\infty)} \times G^{(\infty)} \times G^{(\infty)} \ar[r]^(.76){m(m\times m)} & G^{(\infty)},} \]
where the structure of a group object on $G^{(\infty)}$ is given by the triple $(m, i, e)$.
\end{example}

\subsection{Homotopes of rings and pro-rings}
Let $R$ be an arbitrary ring and let \(S\) be some fixed multiplicative subset of $R$ containing a unit. Denote by $\mathcal{S}$ the category, whose objects are the elements of \(S\) and whose morphisms \(\mathcal{S}(s, s')\) are all \(s'' \in S\) such that \(ss'' = s'\). The composition and the identity morphisms are induced by the ring structure on $R$. It is clear that $\mathcal{S}$ is a filtered category. Unless stated otherwise, all the pro-sets that we encounter in the sequel have \(\mathcal S\) as their category of indices.

We introduce the notion of a {\it homotope} of a ring inspired by a similar notion from nonassociative algebra (cf. McCrimmon?). 
\begin{df} \label{ring-homotope}
 Let $s$ be an element of $R$.  
 By definition, the {\it \(s\)-homotope} of \(R\) is the rng \(R^{(s)} = \{a^{(s)} \mid a \in R\}\) with the operations of addition and multiplication given by
 \[ a^{(s)} + b^{(s)} = (a + b)^{(s)},\ \ a^{(s)} b^{(s)} = (asb)^{(s)},\ a, b\in R.\]
 Clearly, $R^{(s)}$ has the structure of an \(R\)-algebra given by the formula \[a \cdot b^{(s)} = (ab)^{(s)},\ a, b \in R.\] For \(s, s' \in S\) there is a homomorphism of \(R\)-algebras \[R^{(ss')} \to R^{(s')}, a^{(ss')} \mapsto (as)^{(s')}.\]
 Denote by \(R^{(\infty)}\) the formal projective limit of the projective system \(R^{(s)}\), where \(s \in Ob(\mathcal S)\).
 Thus, $R^{(\infty)}$ is an object of the category $\Pro(\Rng)$. 
 It can also be considered as an rng object in \(\Pro(\Set)\).  
\end{df}

Notice that every pro-rng $R^{(\infty)}$ can be considered as a pro-group by forgetting its multiplicative structure pointwise.

\begin{rem}\label{rem:prorings-comment}
 Denote by $sR$ the principal ideal of $R$ generated by $s$. 
 There is an rgn homomorphism $R^{(s)} \to sR$ given by $r^{(s)}\mapsto sr$.
 In the case when $R$ is an integral domain this homomorphism is easily seen to be an rng isomorphism.
 
 The reason why we use homotopes rather than principal ideals in the definition of $R^{(\infty)}$ is that
 there is always a ``division by $s$'' homomorphism of $R$-modules $R^{(ss')} \to R^{(s')}$ given by $r^{(ss')} \mapsto r^{(s')},$
 while the similar map $ss'R \to s'R$ may not exist if $R$ does not happen to be a domain.
 The existence of this division homomorphism will be important in~\cref{sec:local-action}.
 
 Notice also that the projective limit of $R^{(s)}$ in $\Rng$ is often trivial.
 Indeed, if $R$ is a domain, then the limit of $R^{(s)}$ in $\Rng$ computes the intersection of the principal ideals $\bigcap_{s\in S} sR$, which often coincides with the zero ring. 
 This also shows that the set of {\it global elements} of $R^{(\infty)}$ (i.\,e. the hom-set in $\Pro(\Set)$ from the terminal object $1$ to $R^{(\infty)}$) is often trivial and therefore will be of little interest to us.
\end{rem}

Recall that a morphism \(f \in \mathcal C(X, Y)\) is called a split epimorphism (or a retraction) if it admits a section,
 i.\,e. there exists $g \in \mathcal{C}(Y, X)$ such that $fg = \mathrm{id}_{Y}$. Retractions are preserved under pullbacks.

\begin{lemma}\label{RingGeneration}
The rng multiplication morphism $m \colon R^{(\infty)} \times R^{(\infty)} \to R^{(\infty)}$ is a split epimorphism of pro-sets.
\end{lemma}
\begin{proof}
Consider the following pre-morphism of pro-sets:
\[u \colon R^{(\infty)} \to R^{(\infty)} \times R^{(\infty)}, \enskip u^*(s) = s^2, \enskip u^{(s)} \colon c^{(s^2)} \mapsto (1^{(s)}, c^{(s)}).\]
Clearly, this is indeed a pre-morphism and
\[m^{(s)}\bigl(u^{(s)}\bigl(c^{(s^2)}\bigr)\bigr) = 1^{(s)} c^{(s)} = (sc)^{(s)},\]
which shows that $mu = \mathrm{id}_{R^{(\infty)}}$.
\end{proof}

The majority of the calculations encountered in the present article occur in the category of pro-sets or pro-groups.
Most often we need to prove certain equalities between composite pro-set or pro-group morphisms.
It turns out that the usual notation for categorical composition makes these calculations too lengthy and hardly readable. In order to remedy this and also make our computations look like the usual computations with root unipotents in Steinberg groups, we need to introduce a certain way to denote pro-set (pro-group) morphisms, specifically composite ones.

\begin{conv} \label{conv:notation}
First of all, notice that the present conventions apply only to algebraic expressions in which the symbol $(\infty)$ occurs in the upper index of all free variables (e.\,g. the identities of~\cref{RingPresentation} or~\cref{lem:elim-lhs}, but not the identities~\eqref{R1}--\eqref{R4}). We call such expressions {\it pro-expressions}.
 \begin{itemize}
  \item Any pro-expression encountered in the sequel is meant to denote a certain morphism of pro-sets. Apart from the variables marked with the index $(\infty)$, a pro-expression may also involve group or rng operations and other pro-set morphisms.
  \item Whenever a pro-expression does not involve other pro-set morphisms, it should be understood according to~\cref{df-pro-set-morphisms} (the domain and codomain will usually be clear from the context);
  \item To denote the composition of pro-set morphisms we use the syntax of substituted expressions. For example, if $f, g \colon X^{(\infty)} \to Y^{(\infty)}$ are morphisms of pro-groups and $[t_1^{(\infty)}, t_2^{(\infty)}]$ is the pro-group morphism from~\cref{example-commutator}, then $[f(a^{(\infty)}), g(b^{(\infty)})]$ denotes the composite morphism \[[t_1^{(\infty)}, t_2^{(\infty)}] \circ (f\times g) \colon X^{(\infty)} \times X^{(\infty)} \to Y^{(\infty)}.\]  
  \item Any equality of pro-expressions should be understood as the equality of pro-set morphisms defined by these expressions.
  \item The exact names of the variables occuring in a pro-expression are unimportant and are usually chosen arbitrarily. On the other hand, there is always some natural order on the variables that allows one to read the pro-expression unequivocally. In particular, $[t_1^{(\infty)}, t_2^{(\infty)}]$ and $[a^{(\infty)}, b^{(\infty)}]$ denote the same pro-set morphism $G^{(\infty)} \times G^{(\infty)} \to G^{(\infty)}$, while $[t_1^{(\infty)}, t_2^{(\infty)}]$ and $[t_2^{(\infty)}, t_1^{(\infty)}]$ are two different morphisms.
  \item The domain of the pro-set morphism defined by a pro-expression will usually be clear from the context. 
  Most often, it is a power of a single pro-object. In this case to determine the exponent one should count the number of different variables occuring in the expression.
  \item The notation for the multiplication operation is usually suppressed, i.\,e. we prefer the notation $a^{(\infty)} b^{(\infty)}$ to $m(a^{(\infty)}, b^{(\infty)})$ or $a^{(\infty)} \cdot b^{(\infty)}$.
  \item The syntax of tuples is used to denote the product of morphisms. For example, if $f,g \colon X^{(\infty)} \to Y^{(\infty)}$ are morphisms of pro-sets, then the notation $(f(x_1^{(\infty)}), g(x_2^{(\infty)}))$ means simply $f\times g$.
  \item If $g$ is a morphism of pro-sets with $X^{(\infty)} \times Y^{\infty}$ as its domain, then we write $g(a^{(\infty)}, b^{(\infty)})$ instead of $g((a^{(\infty)}, b^{(\infty)}))$.
  \item Notice that the trivial group $1$ is a zero object in the category $\Pro(\Group)$, therefore for any pro-groups $G^{(\infty)}, H^{(\infty)}$ there is a unique morphism $G^{(\infty)} \to H^{(\infty)}$ passing through $1$, this morphism will also be denoted by $1$.
 \end{itemize}
\end{conv} 
Now we are ready to formulate our next result.
\begin{lemma}\label{RingPresentation}
Let \(G^{(\infty)}\) be a pro-group, $R^{(\infty)}$ be a pro-rng and \(g \colon R^{(\infty)} \times R^{(\infty)} \to G^{(\infty)}\) be a morphism of pro-sets. There is a morphism \(f \colon R^{(\infty)} \to G^{(\infty)}\) of pro-groups such that
\[g\bigl(a^{(\infty)} , b^{(\infty)}\bigr) = f\bigl(a^{(\infty)} b^{(\infty)}\bigr)\]
if and only if \(g\) satisfies the following identities in $\Pro(\Set)$:
\begin{itemize}
\item \(\bigl[g\bigl(a_1^{(\infty)}, b_1^{(\infty)}\bigr), g\bigl(a_2^{(\infty)}, b_2^{(\infty)}\bigr)\bigr] = 1\);
\item \(g\bigl(a_1^{(\infty)} + a_2^{(\infty)}, b^{(\infty)}\bigr) = g\bigl(a_1^{(\infty)}, b^{(\infty)}\bigr)\, g\bigl(a_2^{(\infty)}, b^{(\infty)}\bigr)\);
\item \(g\bigl(a^{(\infty)}, b_1^{(\infty)} + b_2^{(\infty)}\bigr) = g\bigl(a^{(\infty)}, b_1^{(\infty)}\bigr)\, g\bigl(a^{(\infty)}, b_2^{(\infty)}\bigr)\);
\item \(g\bigl(a^{(\infty)} b^{(\infty)}, c^{(\infty)}\bigr) = g\bigl(a^{(\infty)}, b^{(\infty)} c^{(\infty)}\bigr)\).
\end{itemize}
\end{lemma}
\begin{proof}
The necessity of the identities is clear.
By~\cref{RingGeneration} the morphism \(f\) is unique, so it suffices to show that it exists.
By~\cref{lem:proobj-is-a-limit} it suffices to consider the case when \(G\) is a group. 
Let \(g\) be a morphism satisfying the above identities.
By definition, there exists $s\in S$ such that $g$ is given by a homomorphism \(g' \colon R^{(s)} \times R^{(s)} \to G\) satisfying the first three identities and the identity 
\[g'\bigl((asb)^{(s)}, c^{(s)}\bigr) = g'\bigl(a^{(s)}, (bsc)^{(s)}\bigr).\]
Consider the map \(f' \colon R^{(s^2)} \to G\) given by
\[f'\bigl(c^{(s^2)}\bigr) = g'\bigl(1^{(s)}, c^{(s)}\bigr),\]
it is a homomorphism by the first and the third identities.
From the last two identities we conclude that for all \(a, b \in R\) one has
\begin{align*}
f'\bigl(a^{(s^2)} b^{(s^2)}\bigr)
&= g' \bigl( 1^{(s)}, (s^2 ab)^{(s)} \bigr) =\\
&= g' \bigl( (sa)^{(s)}, (sb)^{(s)} \bigr) =\\
&= g' \bigl(a^{(s^2)}, b^{(s^2)}\bigr).
\end{align*}
It is clear that \(f'\) defines the required morphism \(f\) of pro-groups.
\end{proof}

\subsection{Steinberg groups and Steinberg pro-groups}
Let $\Phi$ be an irreducible root system of rank $\geq 3$.
We assume that the root system is $\Phi$ contained in a Euclidean space $V = \mathbb{R}^\ell$ whose scalar product we denote by $(-, -)$.
For a pair of roots $\alpha, \beta \in \Phi$ we denote by $\langle \alpha, \beta \rangle$ the integer $\tfrac{2(\alpha, \beta)}{|\beta|^2}$.

Recall that a root subset $\Sigma \subseteq \Phi$ is called {\it closed} if $\alpha, \beta \in \Sigma$, $\alpha+\beta\in\Phi$ imply $\alpha+\beta\in \Sigma$. A closed root subset $\Sigma$ is called {\it symmetric} (resp. {\it special}) if $\Psi = -\Psi$ (resp. $\Psi \cap -\Psi = \emptyset$). By definition, a {\it root subsystem} $\Psi \subseteq \Phi$ is a symmetric and closed root subset.

We start by recalling the classical definition of the Steinberg group.
\begin{df} \label{def:Steinberg}
Let $R$ be a ring. Recall the {\it Steinberg group $\St(\Phi, R)$} is given by generators $x_\alpha(a)$, where $\alpha \in \Phi$ and $a \in R$ and the following list of defining relations (cf.~\cite{Re75}):
\begin{align}
 x_\alpha(a) \cdot x_\alpha(b)    &= x_\alpha(a+b); \tag{R1} \label{R1} \\
 [x_\alpha(a),\ x_\beta(b)] &= 1, \tag{R2} \label{R2} \\ 
 \multispan2{\hfil if $\alpha + \beta \not\in\Phi \cup \{0\};$} \nonumber \\
 [x_\alpha(a),\ x_\beta(b)] &= x_{\alpha + \beta}(N_{\alpha,\beta} \cdot ab), \tag{R3} \label{R3} \\
 \multispan2{\hfill if $\alpha+\beta\in\Phi$ but $\alpha+2\beta,\ 2\alpha+\beta\not\in\Phi;$} \nonumber \\
 [x_\alpha(a),\ x_\beta(b)] &= x_{\alpha + \beta}(N_{\alpha,\beta} \cdot ab) \cdot x_{2\alpha+\beta}(N_{\alpha,\beta}^{2,1} \cdot a^2b), \tag{R4} \label{R4} \\ \multispan2{ \hfill if $\alpha+\beta,2\alpha+\beta\in\Phi$.} \nonumber  \end{align}
\end{df}
The constants $N_{\alpha,\beta}$ and $N_{\alpha,\beta}^{2,1}$ appearing in the above relations are called the {\it structure constants} of the Chevalley group of type $\Phi$. Let us take a closer a look at them.

First of all, notice that we excluded the case $\Phi=\mathsf{G}_2$ so the only possibilities for $N_{\alpha, \beta}$ appearing in the above relations are $\pm 1$ or $\pm 2$.
Notice that $|N_{\alpha,\beta}| = 2$ only when $\alpha$ and $\beta$ are short but $\alpha+\beta$ is long, in which case we set $\widehat{N}_{\alpha, \beta} = \frac{1}{2} N_{\alpha, \beta}$.
In the other cases $|N_{\alpha, \beta}| = 1$.
Now, by definition, $N_{\alpha,\beta}^{2,1} = N_{\alpha,\beta} \cdot \widehat{N}_{\alpha, \alpha+\beta}$.
It is clear that $|N_{\alpha,\beta}^{2,1}|=1$.

Many different methods of the choice of signs of the structure constants have been proposed in the literature, see e.\,g.~\cite{VP}. 
Regardless of their concrete choice, however, the structure constants always must satisfy certain relations. First of all, recall from~\cite[\S~14]{VP}) that
\begin{equation} \label{eq:sc-ids-sl} N_{\alpha, \beta} = -N_{\beta,\alpha} = - N_{-\alpha, -\beta} = \tfrac{|\alpha+\beta|^2}{|\alpha|^2} N_{\beta, -\alpha-\beta} = \tfrac{|\alpha+\beta|^2}{|\beta|^2} N_{-\alpha-\beta, \alpha}. \end{equation}
These identities will be used in the sequel without explicit reference. 

We also will need another identity for structure constants.
To formulate it succintly, we extend the domain of the structure constant function $N_{-,-}$ by setting $N_{\alpha, \beta} = 0$ whenever $\alpha+\beta\not\in\Phi\setminus\{0\}$.
Now if $\alpha, \beta, \gamma$ is a triple of pairwise linearly independent roots such that $\alpha+\beta+\gamma\neq 0$, then one has 
\begin{equation}\label{eq:cocycle2} N_{\alpha,\beta+\gamma} N_{\beta,\gamma} + N_{\beta,\gamma+\alpha} N_{\gamma,\alpha} + N_{\gamma,\alpha+\beta}N_{\alpha,\beta} = 0. \end{equation}
This identity is an equivalent form of (N9) in~\cite[\S~14]{VP} (cf. also (H4) in~\cite{Re75}).

\begin{rem}\label{rem:uni-rad}
Let $\Sigma \subseteq \Phi$ be a special root subset. It is well-known that the restriction of the canonical map $\St(\Phi, R)\to\GG(\Phi, R)$ to the subgroup \[\mathrm{U}(\Sigma, R) = \langle x_{\alpha}(a) \mid a\in R,\ \alpha\in \Sigma \rangle \leq \St(\Phi, R)\] is injective. Morever, for any chosen linear order on \(\Sigma\) the map $R^{\Sigma} \to \mathrm{U}(\Sigma, R)$ given by $(r_\alpha)_\alpha \mapsto \prod_\alpha x_\alpha(r_\alpha)$ is a bijection. \end{rem}

Notice that the multiplicative identity of $R$ is actually never used in the definition of the Steinberg group, 
 which allows one to use it in the situation when $R$ is an rng.
\begin{df}\label{def:Steinberg-homotope}
 Let $R$ be an ring and $S$ be a multiplicative subset of $R$. Also let $\Phi$ be a root system of rank $\geq 3$. Applying the Steinberg group functor $\St(\Phi, -)$ to the projective system of rngs $R^{(s)}$ (see~\cref{ring-homotope}) we obtain a projective system of groups, whose formal projective limit will be denoted by $\St^{(\infty)}(\Phi, R)$ and will be called the {\it Steinberg pro-group}. 
\end{df}

\begin{rem} \label{rem:pro-Steinberg-comment}
There is a group homomorphism $\St(\Phi, R^{(s)}) \to \St(\Phi, sR)$ given by $x_\alpha^{(s)}(a)\mapsto x_\alpha(sa)$. By~\cref{rem:prorings-comment} this homomorphism is an isomorphism in the case when $R$ is an integral domain. Thus, similarly to pro-rngs, Steinberg pro-groups often do not have global elements.
\end{rem}
 
For every root $\alpha \in \Phi$ there is a ``root subgroup'' morphism in $\Pro(\Group)$
\[x_{\alpha} \colon R^{(\infty)} \to \St^{(\infty)}(\Phi, R).\] 
defined by the pre-morphism $x_\alpha^* = \mathrm{id}_S$, $x_\alpha^{(s)}(a^{(s)}) = x_\alpha(a^{(s)})$.

\begin{df}
 Let $R$ be a ring with a multiplicative system $S$.
 Consider the projective system of relative Chevalley groups (also called congruence subgroups) 
 \[\GG(\Phi, R^{(s)}) := \GG_{sc}(\Phi, R^{(s)} \rtimes \ZZ, R^{(s)}) = \Ker\left(\GG_{sc}(\Phi, R^{(s)} \rtimes \ZZ) \to \GG_{sc}(\Phi, \ZZ)\right)\] with the structure morphisms induced by the structure morphisms of \(R^{(\infty)}\). Define the {\it simply-connected Chevalley pro-group} $\GG^{(\infty)}(\Phi, R)$ as the formal projective limit of this system.
\end{df}

Recall that there is well-defined homomorphism $\mathrm{st}\colon \St(\Phi, R) \to \GG_{sc}(\Phi, R)$ sending each generator $x_\alpha(a)$ to the root unipotent $t_\alpha(a)$. The pro-group analogue \(\mathrm{st} \colon \St^{(\infty)}(\Phi, R) \to \GG^{(\infty)}(\Phi, R)\) of this homomorphism is given by the pre-morphism \(\mathrm{st}^* = \mathrm{id}_S\), \(\mathrm{st}^{(s)}\bigl(x_{\alpha}(a^{(s)})\bigr) = t_\alpha(a^{(s)})\). 

\begin{rem}
 The definition of the group $\GG^{(s)}(\Phi, R)$ can be reformulated in terms of Hopf algebras. Denote by \(H_\Phi\) be the Hopf \(\ZZ\)-algebra corresponding to the group scheme \(\GG_{sc}(\Phi, -)\).
 
 Recall that the coproduct in the category $\Rng$ is given by \[R_1 \otimeshat R_2 = (R_1 \otimes_{\ZZ} R_2) \oplus R_1 \oplus R_2.\]
 Thus, $\Rng$ has the structure of a symmetric monoidal category with zero ring as the unit object and $\otimeshat$ as the tensor product.
 
 We claim that the augmentation ideal \(\Ker(\varepsilon)\) of $H_\Phi$ has the structure of a Hopf algebra object (also called Hopf monoid) in \(\Rng\). The coproduct $\Delta$ and the antipode $S$ are induced from the corresponding morphisms defining the structure of a Hopf algebra on $H_\Phi$. The counit $\varepsilon$ is the unique homomorphism $\Ker(\varepsilon) \to 0$.
 
 Now if $R$ is an arbitary ring and $s \in R$ then there is a canonical isomorphism \(\GG^{(s)}(\Phi, R) \cong \Rng(\Ker(\varepsilon), R^{(s)})\). The structure of a group on $\GG^{(s)}(\Phi, R)$ is then induced from the Hopf monoid structure on $\Ker(\varepsilon)$ by duality.
 For instance, the neutral element in this group is the zero map \(0 \colon \Ker(\varepsilon) \to R^{(s)}\). The product of \(g, h \in \Rng(\Ker(\varepsilon), R^{(s)})\) is the composite map
 \[\Ker(\varepsilon) \xrightarrow{\Delta} \Ker(\varepsilon) \otimeshat \Ker(\varepsilon) \xrightarrow{g \otimeshat h} R^{(s)} \otimeshat R^{(s)} \to R^{(s)}.\]
\end{rem}

\begin{rem}
 To formulate the next lemma, we need to introduce a way of reinterpreting the usual Steinberg relations~\eqref{R2}--\eqref{R4} as relations between the morphisms $x_\alpha$ in the category $\Pro(\Group)$. We call these relations the {\it pro-analogues} of~\eqref{R2}--\eqref{R4}. To obtain these relations one has to add the upper index $(\infty)$ to the free variables $a$, $b$ occuring in~\eqref{R2}--\eqref{R4} and then read the resulting expressions according to~\cref{conv:notation}. 
 
 Notice that the pro-analogue of~\eqref{R1} is the identity $x_\alpha(a^{(\infty)}) x_\alpha(b^{(\infty)}) = x_\alpha(a^{(\infty)} + b^{(\infty)})$, or in the usual notation $m \circ (x_\alpha \times x_\alpha) = x_\alpha \circ +_{R^{(\infty)}}$. It is clear that this relation simply means that $x_\alpha$ is a morphism of group objects in $\Pro(\Set)$, which is a consequence of the condition that $x_\alpha$ is a pro-group morphism.
\end{rem}

\begin{lemma}\label{SteinbergPresentation}
Let \(G^{(\infty)}\) be a pro-group. The morphisms \[x_{\alpha} \colon R^{(\infty)} \to \St^{(\infty)}(\Phi, R), \ \alpha\in \Phi\] ``generate'' $\St^{(\infty)}(\Phi, R)$ in the categorical sense. In other words, to ensure that a pair of morphisms $f_1,f_2\colon\St^{(\infty)}(\Phi, R) \to G^{(\infty)}$ are equal it suffices to verify the equalities $f_1 x_{\alpha} = f_2 x_\alpha$ for all $\alpha\in\Phi$.

To obtain a morphism $f \colon \St^{(\infty)}(\Phi, R) \to G^{(\infty)}$ it suffices to construct a collection of pro-group morphisms \(f_{\alpha} \colon R^{(\infty)} \to G^{(\infty)}\) satisfying the pro-analogues of~\eqref{R2}--\eqref{R4} (in which $x_\alpha$'s are replaced with $f_{\alpha}$'s).
\end{lemma}
\begin{proof}
Notice that by~\cref{lem:proobj-is-a-limit} both of the assertions can be verified in the special case when $G^{(\infty)} = G$ is a group.

Let us verify the first assertion. Since there is only a finite number of roots in $\Phi$ one can find a sufficiently large index $s \in S$ such that the homomorphisms $f_1^{(s)}, f_2^{(s)}\colon \St^{(s)}(\Phi, R) \to G$ become equal after precomposition with $x_\alpha$ for all $\alpha \in \Phi$.
Since the root elements $x_\alpha^{(s)}(a)$ generate $\St^{(s)}(\Phi, R)$ we obtain that the morphisms $f_1$ and $f_2$ are equal.

Let us verify the second assertion. By definition, a morphism $f_\alpha \colon R^{(\infty)} \to G$ corresponds to a single group homomorphism 
 $f'_\alpha \colon R^{(s_\alpha)} \to G$ for some $s_\alpha \in S$. Precomposing each $f'_\alpha$ with the structure morhism $R^{(s)} \to R^{(s_\alpha)}$ for sufficiently large $s \in S$, we obtain a collection of homomorphisms $\widetilde{f}_\alpha \colon R^{(s)} \to G$.
 
Notice that~\eqref{R2}--\eqref{R4} specify only a {\it finite} collection of identities in $\Pro(\Set)$ to which $f_\alpha$'s must satisfy.
Unwinding the definitions, we find a sufficiently large index $s \in S$ such that $\widetilde{f}_\alpha$ satisfy the same identities (with $f_\alpha$'s replaced by $\widetilde{f}_\alpha$'s).
Thus, we obtain a group homomorphism $\St^{(s)}(\Phi, R) \to G$, which, in turn, determines a morphism $\St^{(\infty)}(\Phi, R) \to G$.
\end{proof}
Notice that the assumption that $G^{(\infty)}$ is a pro-group and not merely a group object in $\Pro(\Set)$ is essential in the proof of the above lemma.

\section{Elimination of roots}
Throughtout this section we always assume that \(R\) is an arbitrary commutative ring, 
 \(S \subseteq R\) is a multiplicative subset of $R$ and \(\Phi\) is a root system of rank \(\geq 3\) different from \(\rB_\ell\) and \(\rC_\ell\). 

\begin{lemma}\label{ThreeRoots}
Let \(\alpha, \beta, \gamma \in \Phi\) be a triple of roots having the same length such that $\alpha = \beta + \gamma$.  
Then there exist roots \(\beta_1, \gamma_1 \in \Phi \setminus (\ZZ\beta + \ZZ\gamma)\) having the same length as $\beta$ and, moreover, such that \(\beta_1 + \gamma_1 = \beta\). The roots $\beta, \gamma, \beta_1, \gamma_1$ are contained in a root subsystem $\Phi_0 \subseteq \Phi$, whose type is either \(\rA_3\) or \(\rC_3\). \end{lemma}
\begin{proof}
Denote by $\Phi'$ the subset of $\Phi$ consisting of roots having the same length as $\beta$.
It follows from our assumptions that either $\Phi$ is simply-laced and $\Phi' = \Phi$ or $\Phi = \rF_4$, in which case $\Phi'$ is a root subset isomorphic to $\rD_4$ (notice that $\Phi'$ is closed only if $\beta$ is long). In either case the Dynkin diagram of $\Phi'$ is simply laced and has at least $3$ vertices, which implies the first assertion.

Notice that the smallest root subsystem $\Phi_0$ containing $\alpha, \gamma, \beta_1, \gamma_1$ is irreducible and has rank $3$, which implies that it is either of type  $\rC_3$ (if $\Phi = \rF_4$ and $\beta$ is short) or $\rA_3$ (otherwise). \end{proof}

As an immediate application of the above lemma we prove the following generation result, which is a stronger version of the first claim of~\cref{SteinbergPresentation}.
 \begin{lemma}\label{DoubleRootElimination}  
  Let $\alpha, \beta \in \Phi$ be a pair of nonparallel roots. Denote by \(\Phi_0 \subseteq \Phi\) the rank \(2\) subsystem spanned by $\alpha, \beta \in \Phi$, i.e. \(\Phi_0 = \Phi \cap (\ZZ\alpha + \ZZ\beta)\). The collection of root subgroup morphisms $x_\gamma \colon R^{(\infty)} \to \St^{(\infty)}(\Phi, R)$ for $\gamma \in \Phi\setminus \Phi_0$ generates $\St^{(\infty)}(\Phi, R)$ in the categorical sense. In other words, for any pro-group $G^{(\infty)}$ to show that morphisms $f_1, f_2 \colon \St^{(\infty)}(\Phi, R) \to G^{(\infty)}$ are equal it suffices to show that $f_1x_\gamma = f_2x_\gamma$ for all $\gamma \in \Phi\setminus\Phi_0$.
 \end{lemma}
 \begin{proof}
  Thanks to~\cref{SteinbergPresentation} it suffices to show that $f_1 x_\delta = f_2 x_\delta$ for all $\delta \in \Phi_0$.
  
  Let $\delta$ be a root lying in $\Phi_0$. We claim that $\delta$ can be decomposed as a sum $\gamma_1 + \gamma_2$ for some $\gamma_1,\gamma_2 \in \Phi\setminus\Phi_0$ having the same length as $\delta$. Indeed, in the case when \(\Phi_0\) is of type \(\rA_2\) the assertion follows from~\cref{ThreeRoots}, otherwise it is obvious.  
  It is clear that
  \begin{multline*} f_1(x_\delta(a^{(\infty)}b^{(\infty)})) = [f_1(x_{\gamma_1}(N_{\gamma_1, \gamma_2}a^{(\infty)})),\ f_1(x_{\gamma_2}(b^{(\infty)}))] = \\
  = [f_2(x_{\gamma_1}(N_{\gamma_1, \gamma_2}a^{(\infty)})),\ f_2(x_{\gamma_2}(b^{(\infty)}))] = f_2(x_\delta(a^{(\infty)}b^{(\infty)})), \end{multline*}
  which together with~\cref{RingGeneration} implies the required equality $f_1 x_\delta = f_2 x_\delta$.
 \end{proof}

\begin{df}
We denote by $\St(\Phi\setminus\{\pm \alpha\}, R)$ the group given by generators $x_\beta(a)$, $\beta \neq \pm \alpha$, $a\in R$ and the subset of the set of relations \eqref{R1}--\eqref{R4} consisting of those relations, expressions for which do not contain $x_{\pm\alpha}(a)$.

Similarly to~\cref{def:Steinberg-homotope} one can define the pro-group $\St^{(\infty)}(\Phi \setminus\{\pm \alpha\}, R)$ as
the formal projective limit of the projective system of groups $\St(\Phi\setminus\{\pm \alpha\}, R^{(s)})$ where $s\in S$.
\end{df}

For $\beta \neq \pm\alpha$ we use the same notation $x_\beta$ for the ``root subgroup'' morphisms $R^{(\infty)}\to \St^{(\infty)}(\Phi \setminus\{\pm\alpha\}, R)$.
\begin{rem} \label{rem:xpma-presentation}
 One can obtain the analogue of~\cref{SteinbergPresentation} for the pro-group $\St^{(\infty)}(\Phi\setminus\{\pm\alpha\}, R)$ by repeating the same proof verbatim. In particular, $x_\beta$ for $\beta\neq \pm\alpha$ generate $\St^{(\infty)}(\Phi\setminus\{\pm\alpha\}, R)$ in the categorical sense.
\end{rem}
There is a morphism of pro-groups
$F_\alpha \colon \St^{(\infty)}(\Phi \setminus\{\pm\alpha\}, R) \to \St^{(\infty)}(\Phi, R).$
given by the pre-morphism $F_\alpha^{*} = \mathrm{id}_S$ and the homomorphisms \[F_\alpha^{(s)} \colon \St(\Phi \setminus\{\pm\alpha\}, R^{(s)}) \to \St(\Phi, R^{(s)})\] induced by the obvious embedding of generators.

Notice that, in general, the individual homomorphisms $F_\alpha^{(s)}$ need {\it not} be isomorphisms (at least if $s \neq 1$). On the other hand, as the following result shows, the morphism of pro-groups $F_\alpha$ is often an isomorphism. 
\begin{theorem}\label{SingleRootElimination} For every root \(\alpha \in \Phi\) the morphism $F_\alpha$ is an isomorphism of pro-groups. \end{theorem}
The proof of~\cref{SingleRootElimination} occupies the rest of this subsection.
Our immediate goal is to construct the root subgroup morphisms
\[\widetilde x_{\pm \alpha} \colon R^{(\infty)} \to \St^{(\infty)}(\Phi \setminus \{\pm \alpha\}, R) \] ``missing'' from the presentation of $\St^{(\infty)}(\Phi\setminus\{\pm\alpha\}, R)$. The construction of $\widetilde{x}_{-\alpha}$ is analogous to $\widetilde{x}_\alpha$, so it suffices to construct only the latter.

\begin{df} \label{def:xbg}
Let $\beta, \gamma \in \Phi$ be an arbitrary fixed pair of roots such that $\alpha = \beta+\gamma$ and the length of $\beta$, $\gamma$ is the same as $\alpha$'s. 
Denote by $x_{\beta,\gamma}(b^{(\infty)}, c^{(\infty)})$ the morphism
 $[x_\beta(N_{\beta,\gamma}b^{(\infty)}),\ x_\gamma(c^{(\infty)})]\colon R^{(\infty)} \times R^{(\infty)} \to \St^{(\infty)}(\Phi \setminus\{\pm\alpha\}, R).$
\end{df}
Below we will construct the morphism $\widetilde x_\alpha$ based on the morphism $x_{\beta,\gamma}$, see~\cref{lem:new-root}. However, in order to be able to do this we need the following assertion.

\begin{lemma} \label{lem:elim-lhs}
 The morphism $x_{\beta, \gamma}$ satisfies the following relations:
 \begin{align}  
  [x_{\beta, \gamma}(b^{(\infty)}, c^{(\infty)}),\ x_\delta(d^{(\infty)})] &= 1, \label{R2-bg}\\ 
 \multispan2{\hfil if $\alpha + \delta \not\in\Phi \cup \{0\},\ \delta\neq\alpha;$} \nonumber \\
 [x_{\beta, \gamma}(b^{(\infty)}, c^{(\infty)}),\ x_\delta(d^{(\infty)})] &= x_{\alpha + \delta}(N_{\alpha,\delta} \cdot b^{(\infty)}c^{(\infty)}d^{(\infty)}), \label{R3-bg} \\
 \multispan2{\hfill if $\alpha+\delta\in\Phi$ but $\alpha+2\delta,\ 2\alpha+\delta\not\in\Phi;$} \nonumber \\
 [x_{\beta, \gamma}(b^{(\infty)}, c^{(\infty)}),\ x_\delta(d^{(\infty)})] &= x_{\alpha + \delta}(N_{\alpha,\delta} \cdot b^{(\infty)}c^{(\infty)}d^{(\infty)}) \cdot \label{R4-bg1} \\ & \cdot x_{2\alpha+\delta}(N_{\alpha,\delta}^{2,1} \cdot {b^{(\infty)}}^2{c^{(\infty)}}^2d^{(\infty)}), \nonumber \\ \multispan2{ \hfill if $\alpha+\delta,2\alpha+\delta\in\Phi.$ \nonumber} \\
 [x_\delta(d^{(\infty)}), x_{\beta, \gamma}(b^{(\infty)}, c^{(\infty)})] &= x_{\alpha + \delta}(N_{\delta, \alpha} \cdot b^{(\infty)}c^{(\infty)}d^{(\infty)}) \cdot \label{R4-bg2} \\ & \cdot x_{\alpha+2\delta}(N_{\delta, \alpha}^{2,1} \cdot {b^{(\infty)}}{c^{(\infty)}}{d^{(\infty)}}^2), \nonumber \\ \multispan2{ \hfill if $\alpha+\delta,\alpha+2\delta\in\Phi.$ \nonumber} \end{align}
\end{lemma}
\begin{proof}
 First of all, observe that the above relations are obtained from \eqref{R2}--\eqref{R4} by replacing $x_\alpha(a^{(\infty)})$ with $x_{\beta, \gamma}(b^{\infty}, c^{\infty})$.
 
 Let us first consider the case \(\delta \in \Phi \setminus (\ZZ \beta + \ZZ \gamma)\).
 Notice that the root subset $\Sigma = \Phi \cap (\ZZ_{\geq 0}\beta + \ZZ_{\geq 0}\gamma + \ZZ_{>0}\delta)$ is special and does not contain $\pm\alpha$, $-\beta$ or $-\gamma$. Thus, the relations between the remaining root subgroup morphisms of $\St^{(\infty)}(\Phi\setminus\{\pm\alpha\}, R)$ suffice to rewrite the left-hand side of~\eqref{R2-bg}--\eqref{R4-bg2} as follows:
 \begin{align}
  &\bigl[x_{\beta, \gamma}(b^{(\infty)}, c^{(\infty)}), x_\delta(d^{(\infty)})\bigr] = \label{eq:elim-lhs_1} \\
  %
  &= \up{x_\beta(N_{\beta, \gamma} b^{(\infty)})
   x_\gamma(c^{(\infty)})
   x_\beta(-N_{\beta, \gamma} b^{(\infty)})
   x_\gamma(-c^{(\infty)})}
  {x_\delta(d^{(\infty)})}\,
  x_\delta(-d^{(\infty)}) = \nonumber \\
  %
  &= \prod_{\substack{i\beta + j\gamma + k\delta \in \Phi\\ i, j \geq 0; k > 0}}
  x_{i\beta + j\gamma + k\delta} \bigl(A_{i, j, k} {b^{(\infty)}}^i {c^{(\infty)}}^j {d^{(\infty)}}^k\bigr). \nonumber
 \end{align}
 The integers \(A_{i, j, k}\) in the above formula depend only on the roots \(\beta\), \(\gamma\), \(\delta\) (a priori they also depend on the chosen order of factors). To determine the constants $A_{i,j,k}$, one can compute the commutator $[x_\alpha(1),\ x_\delta(1)]$ in $\St(\Phi, \ZZ)$ via the same procedure as in~\eqref{eq:elim-lhs_1}:
 \begin{equation} \label{eq:elim-lhs_2}
  [x_\alpha(1), x_\delta(1)] = \prod_{\substack{i\beta + j\gamma + k\delta \in \Phi\\ i, j \geq 0; k > 0}}
  x_{i\beta + j\gamma + k\delta}(A_{i, j, k}).
 \end{equation}
  By~\cref{rem:uni-rad} the integers $A_{i,j,k}$ are uniquely determined by~\eqref{eq:elim-lhs_2}.
  It is easy to see that, depending on the relative position of $\alpha$ and $\delta$, the integers $A_{i,j,k}$ coincide with the structure constants in the right-hand sides of~\eqref{R2},~\eqref{R3} or~\eqref{R4}, in particular, $A_{i,j,k}=0$ for $i\neq j$.
  Thus, we obtain that \eqref{R2-bg}--\eqref{R4-bg2} follow from~\eqref{eq:elim-lhs_1}.
 
 It remains to verify Steinberg relations in the case \(\delta \in \Phi \cap (\ZZ \beta + \ZZ \gamma)\).
 By~\cref{ThreeRoots} there exist roots \(\beta_1, \beta_2 \in \Phi \setminus (\ZZ \beta + \ZZ \gamma)\) such that \(|\beta_1| = |\beta_2| = |\beta|\) and \(\beta = \beta_1 + \beta_2\). 
 Recall that the root subsystem $\Phi_0 \subseteq \Phi$ containing $\beta,\gamma,\beta_1,\beta_2$ is of type $\rA_3$ or $\rC_3$. 
 In both cases we may assume that $\alpha + \beta_2 \not\in\Phi$.
 
 Let us first verify the relation~\eqref{R2-bg} in the case $\delta \in \{\beta, \gamma\}$. By symmetry we may assume that $\delta = \beta$. 
 Direct computation shows that
 \begin{align}
  [x_{\beta,\gamma}(b^{(\infty)}, c^{(\infty)}),\ x_\beta(N_{\beta_1, \beta_2} b_1^{(\infty)}b_2^{(\infty)})] \nonumber \\
   = [x_{\beta,\gamma}(b^{(\infty)}, c^{(\infty)}),\ [x_{\beta_1}(b_1^{(\infty)}),\ x_{\beta_2}(b_2^{(\infty)})]]  & \text{ by~\eqref{R3}} \label{eq:elim-lhs3} \\ 
   = [[x_{\beta, \gamma}(b^{(\infty)}, c^{(\infty)}),\ x_{\beta_1}(b_1)],\ \up{x_{\beta_1}(b_1^{(\infty)})} x_{\beta_2}(b_2^{(\infty)})]  & \text{ by~\eqref{eq:HW-corr},\eqref{R2-bg}.} \nonumber \end{align}
In the case $\Phi_0\cong \rA_3$ the inner commutator in the last expression is trivial by~\eqref{R2-bg},
 therefore so is the outer commutator.
In the case $\Phi_0\cong \rC_3$ the last expression can be further simplified using~\eqref{R3} and the already proved relation~\eqref{R3-bg} as follows:
\[ \ldots = [x_{\alpha+\beta_1}(N_{\alpha, \beta_1} b^{(\infty)}c^{(\infty)}b_1^{(\infty)}),\ x_{\beta}(N_{\beta_1, \beta_2} b_1^{(\infty)} b_2^{(\infty)}) x_{\beta_2}(b_2^{(\infty)})]. \]
It is clear that the latter commutator is trivial by~\eqref{eq:comm-mult-rhs} and~\eqref{R2-bg}.  
  In both cases the right-hand side of~\eqref{eq:elim-lhs3} is trivial. Consequently, from~\cref{RingGeneration} we obtain that
 $[x_{\beta,\gamma}(b^{(\infty)}, c^{(\infty)}),\ x_\beta(d^{(\infty)})] = 1,$
 which completes the proof of~\eqref{R2-bg}. 
 
 Finally, it remains to verify~\eqref{R3-bg} in the case $\delta \in \{-\beta, -\gamma\}$.
 By symmetry it suffices to consider the case $\delta = -\beta$.
 From the already proved relations~\eqref{R2-bg}--\eqref{R3-bg} and the other Steinberg relations one obtains that
 \begin{align*}
  &[x_{\beta, \gamma}(b^{(\infty)}, c^{(\infty)}),
  x_{-\beta}(N_{-\beta_1, -\beta_2} b_1^{(\infty)} b_2^{(\infty)})] = \\
  %
  &= [\up{x_{\beta, \gamma}(b^{(\infty)}, c^{(\infty)})}
   {x_{-\beta_1}(b_1^{(\infty)})},
  \up{x_{\beta, \gamma}(b^{(\infty)}, c^{(\infty)})}
   {x_{-\beta_2}(b_2^{(\infty)})}]\,
  x_{-\beta}(-N_{-\beta_1, -\beta_2} b_1^{(\infty)} b_2^{(\infty)})\\
  %
  &= \prod_{\substack{i\alpha - j\beta_1 - k\beta_2 \in \Phi\\ i, j, k \geq 0\\ (i, j, k) \neq (0, 0, 0)}}
  x_{i\alpha - j\beta_1 - k\beta_2}\bigl(B_{i, j, k} {b^{(\infty)}}^i {c^{(\infty)}}^i {b_1^{(\infty)}}^j {b_2^{(\infty)}}^k\bigr),  
 \end{align*}
for some integers $B_{i,j,k}$.
Direct computation (or an argument similar to the one used in the first part of the proof) shows that the constants \(B_{i, j, k}\) are all zero with the sole exception of \(B_{1, 1, 1}$, which is equal to $N_{\alpha, -\beta}\). Consequently, from~\cref{RingGeneration} we obtain that
 \[[x_{\beta, \gamma}(b^{(\infty)}, c^{(\infty)}), x_{-\beta}(d^{(\infty)})] = x_\gamma(N_{\alpha, -\beta} b^{(\infty)} c^{(\infty)} d^{(\infty)}),\]
which finishes the proof of~\eqref{R3-bg}.
\end{proof}

\begin{lemma}\label{lem:new-root}
 The morphism $x_{\beta, \gamma}$ satisfies the identities listed in~\cref{RingPresentation} and therefore gives rise to a pro-group morphism $R^{(\infty)} \to \St^{(\infty)}(\Phi\setminus\{\pm\alpha\}, R),$ which we denote by $\widetilde{x}_\alpha$. The resulting morphism $\widetilde{x}_\alpha$ does not depend on the choice of $\beta$ and $\gamma$.
\end{lemma}
\begin{proof}
 First of all, observe that~\eqref{R2-bg} implies the identity \[[x_{\beta, \gamma}(b_1^{(\infty)}, c_1^{(\infty)}),
 x_{\beta, \gamma}(b_2^{(\infty)}, c_2^{(\infty)})] = 1.\] 
 Notice also that~\eqref{eq:comm-mult-lhs} and~\eqref{R2-bg} imply that
 \begin{align*}
 x_{\beta, \gamma}\bigl(b_1^{(\infty)} + b_2^{(\infty)}, c^{(\infty)}\bigr)
 = \bigl[x_\beta(N_{\beta, \gamma} b_1^{(\infty)})
 x_\beta(N_{\beta, \gamma} b_2^{(\infty)}),
 x_\gamma(c^{(\infty)})\bigr]\\
 = x_{\beta, \gamma}(b_1^{(\infty)}, c^{(\infty)})\,
 x_{\beta, \gamma}(b_2^{(\infty)}, c^{(\infty)}).
 \end{align*}
 Similarly, one can show the equality
 \[x_{\beta, \gamma}\bigl(b^{(\infty)}, c_1^{(\infty)} + c_2^{(\infty)}\bigr)
 = x_{\beta, \gamma}(b^{(\infty)}, c_1^{(\infty)})\,
 x_{\beta, \gamma}(b^{(\infty)}, c_2^{(\infty)}).\]
 Thus, the morphism \(x_{\beta, \gamma}\) satisfies the first three requirements of~\cref{RingPresentation}. 
 
 Now suppose that \(\alpha = \beta_1 + \gamma_1 = \beta_2 + \gamma_2\) are two different decompositions for $\alpha$ such that $\alpha$, $\beta_i$ and $\gamma_i$ have the same length and \(\alpha\), \(\beta_1\), \(\beta_2\) are linearly independent. By~\cref{ThreeRoots} such decompositions exist and the roots $\beta_i$, $\gamma_i$ are contained in a root subsystem $\Phi_0$ of type \(\rA_3\) or \(\rC_3\). Swapping $\beta_1$ with $\gamma_1$, if necessary, we also may assume that $\beta_1$ and $\beta_2$ form an acute angle. Set $\delta = \gamma_1 - \gamma_2 = \beta_2 - \beta_1$ and \[\varepsilon_1 = N_{\beta_1, \gamma_1},\ \varepsilon_2 = N_{\beta_2, \gamma_2},\ \varepsilon_3 = N_{\delta,\gamma_2},\ \varepsilon_4 = N_{\beta_1, \delta}.\]
 
In order to simplify keeping track of the relative angles and the length of the roots, the reader may assume that  $\beta_i$, $\gamma_i$ are concretely realized in the space $\mathbb{R}^3$ as follows:
\(\beta_1 = \mathrm e_1 - \mathrm e_2,\) \(\gamma_1 = \mathrm e_2 - \mathrm e_3\) and
 \begin{itemize}
 \item $\beta_2 = \mathrm e_1 - \mathrm e_4$, $\gamma_2 = \mathrm e_4 - \mathrm e_3$ in the case \(\Phi_0\cong\rA_3\), \item $\beta_2 = \mathrm e_1 + \mathrm e_2$, $\gamma_2 = -\mathrm e_2 - \mathrm e_3$ in the case \(\Phi_0\cong\rC_3\).
\end{itemize}
Here $\mathrm e_i$ denote the standard basis vectors of $\mathbb{R}^3$ and we assume that the root systems $\rA_3$ and $\rC_3$ are realized in $\mathbb{R}^3$ as in~\cite[Ch.~VI,~\S\S~4.6--4.7]{Bou81}. 

 Substituting the triple $(\beta_1, \gamma_1, -\beta_2)$ into~\eqref{eq:cocycle2}, it is not hard to conclude that in both cases one has $\varepsilon_1 \varepsilon_2 \varepsilon_3 \varepsilon_4 = 1$. Now direct calculation shows that
 \begin{align*}
x_{\beta_1, \gamma_1}(b^{(\infty)}, c^{(\infty)} d^{(\infty)}) = [x_{\beta_1}(\varepsilon_1b^{(\infty)}), x_{\gamma_1}(c^{(\infty)} d^{(\infty)})] & \nonumber \\
= [x_{\beta_1}(\varepsilon_1b^{(\infty)}), [x_{\delta}(\varepsilon_3c^{(\infty)}), x_{\gamma_2}(d^{(\infty)})]] &\text{  by~\eqref{R3} or~\eqref{R2},\eqref{R4},\eqref{eq:comm-mult-rhs}.} \nonumber \\ 
= [[x_{\beta_1}(\varepsilon_1b^{(\infty)}),\ x_\delta(\varepsilon_3c^{(\infty)})],\ {}^{x_\delta(\varepsilon_3c^{(\infty)})}x_{\gamma_2}(d^{(\infty)})] & \text{ by~\eqref{R2},\eqref{eq:HW-corr}}\\
= [x_{\beta_2}(\varepsilon_2b^{(\infty)}c^{(\infty)}),\ x_{\gamma_2}(d^{(\infty)}) x_{\gamma_1}(c^{(\infty)}d^{(\infty)}) ] & \text{ by~\eqref{R3}}\\
= [x_{\beta_2}(\varepsilon_2b^{(\infty)}c^{(\infty)}),\ x_{\gamma_2}(d^{(\infty)})] &\text{ by~\eqref{R2},\eqref{eq:comm-mult-rhs}} \\
= x_{\beta_2, \gamma_2}(b^{(\infty)} c^{(\infty)}, d^{(\infty)}). & \end{align*}

 Thus, in both cases we obtain that
 \begin{equation}\label{eq:balance}
 x_{\beta_1, \gamma_1}(b^{(\infty)}, c^{(\infty)} d^{(\infty)}) = x_{\beta_2, \gamma_2}(b^{(\infty)} c^{(\infty)}, d^{(\infty)}).
 \end{equation}
 It follows from~\eqref{eq:balance} that $x_{\beta_1,\gamma_1}(b^{(\infty)}, u_1^{(\infty)}u_2^{(\infty)}d^{(\infty)}) = x_{\beta_1,\gamma_1}(b^{(\infty)}u_1^{(\infty)}u_2^{(\infty)},d^{(\infty)})$ therefore from~\cref{RingGeneration} we obtain that
 \[x_{\beta_1, \gamma_1}(b^{(\infty)}, u^{(\infty)} c^{(\infty)}) = x_{\beta_1, \gamma_1}(b^{(\infty)} u^{(\infty)}, c^{(\infty)}).\]
 Thus, the last requirement of~\cref{RingPresentation} is satisfied. Consequently, there exists a unique morphism of pro-groups \(\widetilde x_\alpha \colon R^{(\infty)} \to \St^{(\infty)}(\Phi \setminus \{\pm \alpha\}, R)\) satisfying
 \[x_{\beta_1, \gamma_1}(b^{(\infty)}, c^{(\infty)}) = \widetilde x_\alpha(b^{(\infty)} c^{(\infty)}) = x_{\beta_2, \gamma_2}(b^{(\infty)}, c^{(\infty)}). \qedhere\]
\end{proof}

The next step in the proof of~\cref{SingleRootElimination} is to verify that $\widetilde{x}_\alpha$ satisfies the relations~\eqref{R2}--\eqref{R4}.
Notice that none of these relations simultaneously involves both \(\alpha\) and \(-\alpha\).
Thus, by symmetry it suffices to verify only Steinberg relations involving \(\alpha\).
Combining \cref{lem:elim-lhs,lem:new-root} we immediately obtain the following.
\begin{corollary} \label{cor:elim-lhs}
 The root subgroup morphism $\widetilde{x}_\alpha$ satisfies the pro-analogues of Steinberg relations of type~\eqref{R2}--\eqref{R4}, in which it occurs on the left-hand side.
\end{corollary}

Thus, to finish the proof of~\cref{SingleRootElimination} it suffices to consider the case when $\widetilde{x}_\alpha$ occurs in the right-hand side of the commutator formula.
\begin{lemma} \label{lem:elim-rhs-r4}
 The root subgroup morphism $\widetilde{x}_\alpha$ satisfies the pro-analogues of Steinberg relations of type~\eqref{R4} in which it occurs on the right-hand side.
\end{lemma}
\begin{proof}
We only need to consider the case $\Phi = \rF_4$.
We need to verify the relation obtained from \begin{equation}\label{eq:elim-rhs-r4-1} [x_{\beta}(b^{(\infty)}),\ x_{\gamma}(c^{(\infty)})] = x_{\beta+\gamma}(N_{\beta,\gamma}b^{(\infty)} c^{(\infty)}) x_{2\beta+\gamma}(N_{\beta,\gamma}^{2,1}{b^{(\infty)}}^2c^{(\infty)})\end{equation} by replacing either $x_{\beta+\gamma}$ or $x_{2\beta+\gamma}$ with $\widetilde{x}_{\alpha}$.

First, let us consider the case \(\alpha = \beta + \gamma\), in which \(\alpha\), \(\beta\) are short and \(\gamma\) is long. Consider a decomposition \(\beta = \beta_1 + \beta_2\) for some short roots \(\beta_i\). The smallest root subsystem containing \(\beta_i\) and \(\gamma\) is of type \(\rC_3\), so we may assume that \(\alpha = \mathrm e_1 + \mathrm e_3\), \(\beta = \mathrm e_1 - \mathrm e_3\), \(\beta_1 = \mathrm e_1 - \mathrm e_2\), \(\beta_2 = \mathrm e_2 - \mathrm e_3\), \(\gamma = 2\mathrm e_3\). Set $\varepsilon_1 = N_{\beta_1, \beta_2},$ $\varepsilon_2 = N_{\beta_2,\gamma}^{2,1},$ $\varepsilon_3 = N_{\beta_2, \gamma},$ $\varepsilon_4 = N_{\beta_1, 2\beta_2+\gamma}^{2,1},$ $\varepsilon_5 = N_{\beta_1, 2\beta_2+\gamma},$ $\varepsilon_6 = N_{\beta_1,\beta_2+\gamma},$ $\varepsilon_7 = N_{\beta_2+\gamma, \beta}.$ From~\eqref{R4} we immediately obtain that
 \begin{multline*}
  \bigl[x_\gamma(c^{(\infty)}), x_\beta(\varepsilon_1 b_1^{(\infty)} b_2^{(\infty)})\bigr]
  = \bigl[x_{\beta_1}(b_1^{(\infty)}), \up{x_\gamma(c^{(\infty)})} {x_{\beta_2}(b_2^{(\infty)})}\bigr]\,
  x_\beta(-\varepsilon_1 b_1^{(\infty)} b_2^{(\infty)}) \\
  =[x_{\beta_1}(b_1^{(\infty)}),\ x_{2\beta_2+\gamma}(-\varepsilon_2{b_2^{(\infty)}}^2c^{(\infty)}) x_{\beta_2+\gamma}(-\varepsilon_3b_2^{(\infty)}c^{(\infty)}) x_{\beta_2}(b_2^{(\infty)})] x_{\beta}(-\varepsilon_1b_1b_2) \end{multline*}
 Direct computation involving~\eqref{eq:comm-mult-rhs}, \cref{cor:elim-lhs} and relations~\eqref{R2}--\eqref{R4} shows that the latter expression further simplifies to
 \begin{multline*}  x_{2\beta + \gamma}( - \varepsilon_2 \varepsilon_4 {b_1^{(\infty)}}^2{b_2^{(\infty)}}^2c^{(\infty)}) x_{\beta_1 + 2\beta_2 + \gamma}(-(\varepsilon_2\varepsilon_5 +\varepsilon_1\varepsilon_3\varepsilon_7) b_1^{(\infty)}{b_2^{(\infty)}}^2c^{(\infty)}) \cdot \\ \cdot \widetilde{x}_{\alpha}(-\varepsilon_3 \varepsilon_6 b_1^{(\infty)}b_2^{(\infty)}c^{(\infty)}).\end{multline*}
Substituting the triples $(\beta_1, \beta_2+\gamma, \beta_2)$, $(\beta_1, \beta_2, \gamma)$, $(\beta_1, \beta_1+\beta_2, \beta_2+\gamma)$ into~\eqref{eq:cocycle2} we obtain the equalities \[\varepsilon_2 \varepsilon_3 \varepsilon_5 = - \varepsilon_1 \varepsilon_7,\ \varepsilon_3 \varepsilon_6  = N_{\beta, \gamma}\varepsilon_1,\ 2 \varepsilon_4 \varepsilon_5 \varepsilon_7 = - \varepsilon_6 N_{\beta,\alpha}.\] Together with~\cref{RingGeneration} they imply the identity \[[x_\gamma(c^{(\infty)}), x_\beta(b^{(\infty)})] = 
 \widetilde{x}_\alpha(-N_{\beta, \gamma} b^{(\infty)} c^{(\infty)}) x_{2\beta+\gamma}(-N_{\beta,\gamma}^{2,1} {b^{(\infty)}}^2 {c^{(\infty)}}^2),\] which is equivalent to~\eqref{eq:elim-rhs-r4-1}. 
 
 Now consider the case \(\alpha = 2\beta + \gamma\), in which \(\beta\) is short and \(\alpha\), \(\gamma\) are long. We can choose a decomposition \(\gamma = \gamma_1 + \gamma_2\) for some long roots \(\gamma_i\). The smallest root subsystem containing \(\beta\) and \(\gamma_i\) is of type \(\rB_3\), so we may assume that \(\alpha = \mathrm e_1 + \mathrm e_3\), \(\beta = \mathrm e_3\), \(\gamma = \mathrm e_1 - \mathrm e_3\), \(\gamma_1 = \mathrm e_1 - \mathrm e_2\), \(\gamma_2 = \mathrm e_2 - \mathrm e_3\). Set $\varepsilon_1 = N_{\gamma_1, \gamma_2}$, $\varepsilon_2 = N_{\beta,\gamma_2}^{2,1}$, $\varepsilon_3 = N_{\beta,\gamma_2}$, $\varepsilon_4 = N_{\gamma_1, 2\beta+\gamma_2}$, $\varepsilon_5 = N_{\gamma_1, \beta+\gamma_2}$.
 Again, direct computating involving~\eqref{eq:comm-mult-rhs}, \cref{cor:elim-lhs} and relations~\eqref{R2}--\eqref{R4} shows that
 \begin{multline*}
  \bigl[x_\beta(b^{(\infty)}), x_\gamma(\varepsilon_1 c_1^{(\infty)} c_2^{(\infty)})\bigr]
   =  \bigl[x_{\gamma_1}(c_1^{(\infty)}), \up{x_\beta(b^{(\infty)})} {x_{\gamma_2}(c_2^{(\infty)})}\bigr]\,
  x_\gamma(-\varepsilon_1 c_1^{(\infty)} c_2^{(\infty)}) \\  
  = \bigl[x_{\gamma_1}(c_1^{(\infty)}), x_{2\beta+\gamma_2}(\varepsilon_2 {b^{(\infty)}}^2 c_2^{(\infty)}) x_{\beta+\gamma_2}(\varepsilon_3 b^{(\infty)} c_2^{(\infty)}) x_{\gamma_2}(c_2^{(\infty)})\bigr] x_\gamma(-\varepsilon_1 c_1^{(\infty)} c_2^{(\infty)}) \\
  = \widetilde{x}_\alpha( \varepsilon_2 \varepsilon_4 {b^{(\infty)}}^2 c_1^{(\infty)}c_2^{(\infty)}) \cdot x_{\beta+\gamma}(\varepsilon_3 \varepsilon_5 b^{(\infty)} c_1^{(\infty)}c_2^{(\infty)}). \end{multline*}
 Substituting the triples $(\beta, \gamma_2, \gamma_1)$, $(\beta, \beta+\gamma_2, \gamma_1)$ into~\eqref{eq:cocycle2} we obtain the identities $\varepsilon_3 \varepsilon_5 = \varepsilon_1 N_{\beta,\gamma}$ and
 $2\varepsilon_2\varepsilon_3 \varepsilon_4 = \varepsilon_5N_{\beta,\beta+\gamma},$ which together with~\cref{RingGeneration} imply~\eqref{eq:elim-rhs-r4-1}. \end{proof}

\begin{lemma} \label{lem:elim-rhs-r3}
 The root subgroup morphism $\widetilde{x}_\alpha$ satisfies the pro-analogues of Steinberg relations~of type \eqref{R3} in which it occurs on the right-hand side.
\end{lemma}
\begin{proof}
We need to verify the relation 
\begin{equation}\label{eq:elim-rhs-r3-1} [x_{\beta}(b^{(\infty)}),\ x_{\gamma}(c^{(\infty)})] = \widetilde{x}_{\alpha}(N_{\beta,\gamma} b^{(\infty)}c^{(\infty)}).\end{equation}
In the case when $\alpha$, $\beta$ and $\gamma$ have the same length the assertion follows from \cref{lem:new-root}. Thus, we only need to consider the case when \(\alpha = \beta + \gamma\) and \(\alpha\) is long while \(\beta\) and \(\gamma\) are short. The smallest root subsystem containing \(\alpha\), \(\beta\), \(\gamma\) is of type \(\rB_2\). Without loss of generality we may assume \(\alpha = \mathrm e_1 + \mathrm e_2\), \(\beta = \mathrm e_1\), and \(\gamma = \mathrm e_2\).
Set $\varepsilon_1 = N_{\beta,\gamma-\beta}^{2,1}$, $\varepsilon_2 = N_{\beta,\gamma-\beta}$. Direct computation shows that \begin{align*}
  \up{x_\beta(d^\infty)} x_\gamma(\varepsilon_2b^{(\infty)}c^{(\infty)}) \cdot \widetilde{x}_\alpha(\varepsilon_1 {b^{(\infty)}}^2{c^{(\infty)}}) \\
  = \up{x_\beta(d^{(\infty)})}
   {\bigl(x_\gamma(\varepsilon_2 b^{(\infty)} c^{(\infty)})\,
   \widetilde x_\alpha(\varepsilon_1
   {b^{(\infty)}}^2 c^{(\infty)})\bigr)} & \text{ by \cref{cor:elim-lhs}}\\
  = \bigl[x_\beta(b^{(\infty)}),
  \up{x_\beta(d^{(\infty)})}
   {x_{\gamma - \beta}(c^{(\infty)})}\bigr] & \text{ by~\eqref{R2}, \cref{lem:elim-rhs-r4}}\\
  = \up{x_\beta(b^{(\infty)} + d^{(\infty)})}
   {x_{\gamma - \beta}(c^{(\infty)})}\,
  \up{x_\beta(d^{(\infty)})}
   {x_{\gamma - \beta}(-c^{(\infty)})} & \text{ by~\eqref{R1}} \\  
  = x_{\gamma}(\varepsilon_2 b^{(\infty)}c^{(\infty)}) \widetilde{x}_{\alpha}(2\varepsilon_1{b^{(\infty)}}{d^{(\infty)}}) \widetilde{x}_\alpha(\varepsilon_1 {b^{(\infty)}}^2{c^{(\infty)}}) & \text{ by~\cref{lem:elim-rhs-r4}}
 \end{align*}
The relation~\eqref{eq:elim-rhs-r3-1} now follows from \cref{RingGeneration} and the identity $2\varepsilon_1 = \varepsilon_2 N_{\beta, \gamma}$. \end{proof} 

\begin{proof}[Proof of~\cref{SingleRootElimination}]
To help distinguish between the root subgroup morphisms of $\St^{(\infty)}(\Phi, R)$ and $\St^{(\infty)}(\Phi\setminus\{\pm\alpha\}, R)$ we rename the root subgroup morphisms $x_\beta$, $\beta\neq\pm\alpha$ of $\St(\Phi\setminus\{\pm\alpha\}, R^{(\infty)})$ to $\widetilde{x}_{\beta}$. For the morphisms $x_\beta$ of $\St^{(\infty)}(\Phi, R)$ we continue to use the usual notation. 

By~\cref{SteinbergPresentation} the morphisms $\widetilde{x}_{\beta}$ give rise to a morphism $G_\alpha \colon \St^{(\infty)}(\Phi, R) \to \St^{(\infty)}(\Phi\setminus\{\pm\alpha\}, R)$. By definition, $G_\alpha x_\beta = \widetilde{x}_\beta$ for all $\beta$. On the other hand, it is clear that $F_\alpha \widetilde{x}_\beta = x_\beta$ for $\beta\neq \pm\alpha$. To see that $G_\alpha$ is inverse to $F_\alpha$ it remains to invoke the first part of~\cref{SteinbergPresentation} and~\cref{rem:xpma-presentation}.
\end{proof}


\section{The action of localized groups on pro-groups} \label{sec:local-action}
Throughout this section \(R\) is a ring and \(S \subseteq R\) is a multiplicative subset.
\subsection{The case of Chevalley groups}
Our first goal is to show that \(\GG_{sc}(\Phi, S^{-1} R)\) can be made to act on the Chevalley pro-group \(\GG^{(\infty)}(\Phi, R)\) by conjugation. Denote by \(H_\Phi\) the Hopf \(\ZZ\)-algebra of \(\GG_{sc}(\Phi, -)\) with the structure of a Hopf algebra given by the triple $(\Delta, S, \varepsilon)$. Recall that \(H_\Phi\) is a finitely presented commutative \(\ZZ\)-algebra, therefore $\Ker(\varepsilon)$ is at least a finitely generated rng. Consider the ``coconjugation'' homomorphism (written down in Sweedler notation)
\[\mathrm{Coconj} \colon \Ker(\varepsilon) \to H_\Phi \otimes \Ker(\varepsilon),\ h \mapsto \sum h_{(1)} S(h_{(3)}) \otimes h_{(2)}.\]
Now let $g$ be an element of $\mathbf{Ring}(H_\Phi, S^{-1}R) \cong \GG_{sc}(\Phi, S^{-1} R)$.
Consider the homomorphism $\mathrm{Coconj}_g$ of ``coconjugation by $g$'', which is defined as the composite of the following two rng homomorphisms:
\[\xymatrix{\Ker(\varepsilon) \ar[r]^(.4){\mathrm{Coconj}} & H_\Phi \otimes \Ker(\varepsilon) \ar[r]^(0.45){g\otimes\mathrm{id}} & S^{-1}R \otimes \Ker(\varepsilon).}\]
Since $\Ker(\varepsilon)$ is finitely generated, there exists $s_0 \in S$ such that the image of every generator $x_i$ of $\Ker(\varepsilon)$ under $\mathrm{Coconj}_g$ can be written as $\sum_j \frac{r_j}{s_0} \otimes x_{ij}$.

We are ready to construct the automorphism $\GG^{(\infty)}(\Phi, R) \to \GG^{(\infty)}(\Phi, R)$ of ``conjugation by $g$''. By definition, this amounts to constructing a collection of homomorphisms
$\Rng(\Ker(\varepsilon), R^{(f(s))}) \to \Rng(\Ker(\varepsilon), R^{(s)})$ for some function $f \colon S \to S$. Set $f(s) = ss_0$ and let $h$ be an element of $\Rng(\Ker(\varepsilon), R^{(ss_0)})$. It is clear that the composite homomorphism
\[\xymatrix{ \Ker(\varepsilon) \ar[r]^(0.4){\mathrm{Coconj}_g} & S^{-1}R \otimes \Ker(\varepsilon) \ar[r]^{\mathrm{id}\otimes h} & S^{-1}R \otimes R^{(ss_0)} \ar[r] & S^{-1}R \otimes_R R^{(ss_0)}}\]
lands in the $R$-submodule $A_{s_0} = \langle \frac{r}{s_0} \otimes r'^{(ss_0)}\mid r, r' \in R \rangle$ of $S^{-1}R \otimes_R R^{(ss_0)}$. Here $A_{s_0}$ is, in fact, a subring of $S^{-1}R \otimes_R R^{(ss_0)}$. To obtain the required element $\up g h$ it remains to postcompose the above arrow with the homomorphism $A_{s_0} \to R^{(s)}$ defined on tensors via $\frac{r}{s_0} \otimes r'^{(ss_0)} \mapsto rr'^{(s)}$. It can be checked directly that the described construction produces the sought group action.

\subsection{The case of Steinberg groups}
Clearly, the set $\Pro(\Group)(R^{(\infty)})$ of endomorphisms of the additive pro-group of the pro-rng $R^{(\infty)}$ can be endowed with the structure of an associative ring. The addition is given by  $(f, g) \mapsto (+_{R^{(\infty)}}) \circ (f\times g) \circ \Delta$, while the multiplication is the usual composition of endomorphisms.

The pro-ring $R^{(\infty)}$ can be turned into an \(S^{-1} R\)-algebra in the following manner. For every class of fractions \([\frac rs] \in S^{-1} R\) there is a well-defined pro-group endomorphism \(m_{[\frac rs]} \colon R^{(\infty)} \to R^{(\infty)}\) given by \(m_{[\frac rs]}^*(s') = ss'\) and \(m_{[\frac rs]}^{(s')}(a^{(ss')}) = (ra)^{(s')}\). It is easy to see that $m_{[\frac{r}{s}]}$ does not depend on the choice of the representative \(\tfrac r s\). Moreover, it is easy to see that \(m\) is actually a homomorphism of rings \(S^{-1} R \to \Pro(\Group)(R^{(\infty)})\) and that 
\begin{equation} \label{eq:m-mult} m_{[\frac rs]}(a^{(\infty)} b^{(\infty)}) = m_{[\frac rs]}(a^{(\infty)}) b^{(\infty)} = a^{(\infty)} m_{[\frac rs]}(b^{(\infty)}).\end{equation}
For shortness we write \(\frac rs a^{(\infty)}\) instead of \(m_{[\frac rs]}(a^{(\infty)})\). 

Our next step is to construct the action of the Steinberg group $\St(\Phi, S^{-1}R)$ on the Steinberg pro-group $\St^{(\infty)}(\Phi, R)$.
\begin{df}\label{root-action}
 Let \(R\) be a ring, \(S \subseteq R\) be a multiplicative subset, and \(\Phi\) be a root system of rank \(\geq 3\) different from \(\rB_\ell\) and \(\rC_\ell\).
 
 For $u \in S^{-1}R$ and a root subgroup morphism $x_\beta$ of $\St^{(\infty)}(\Phi\setminus\{\pm\alpha\}, R)$ we define the morphism 
 $\up{x_\alpha(u)}x_\beta \colon R^{(\infty)} \to \St^{(\infty)}(\Phi\setminus\{\pm\alpha\}, R)$
 via one of the following identities:
 \begin{align*}
 \up{x_\alpha(u)}{x_\beta(b^{(\infty)})}
 &:= x_\beta(b^{(\infty)}), \\
 \multispan2{\hfil if $\alpha + \beta \notin \Phi \cup \{0\}$;} \\
 %
 \up{x_\alpha(u)}{x_\beta(b^{(\infty)})}
 &:= x_\beta(b^{(\infty)})
 x_{\alpha + \beta}\bigl(N_{\alpha, \beta} u b^{(\infty)}\bigr), \\
 \multispan2{\hfill if $\alpha + \beta \in \Phi$ but $\alpha + 2\beta, 2\alpha + \beta \notin \Phi$;} \\
 %
 \up{x_\alpha(u)}{x_\beta(b^{(\infty)})}
 &:= x_\beta(b^{(\infty)})
  x_{\alpha + \beta}\bigl(N_{\alpha, \beta} u b^{(\infty)}\bigr)
  x_{2\alpha + \beta}\bigl(N^{2,1}_{\alpha, \beta} u^2 b^{(\infty)}\bigr), \\
 \multispan2{\hfill if $\alpha + \beta, 2\alpha + \beta \in \Phi$;} \\
 %
 \up{x_\alpha(u)}{x_\beta(b^{(\infty)})}
 &:= x_\beta(b^{(\infty)})
  x_{\alpha + \beta}\bigl(N_{\alpha, \beta} u b^{(\infty)}\bigr)
  x_{\alpha + 2\beta}\bigl(-N^{2,1}_{\beta, \alpha} u {b^{(\infty)}}^2\bigr), \\
 \multispan2{\hfill if $\alpha + \beta, \alpha + 2\beta \in \Phi$.}
 \end{align*} 
\end{df}

\begin{prop}\label{SteinbergLocalAction} 
 Let $R$ and $\Phi$ be as in the above definition.
 The above identities specify a well-defined conjugation action of the group \(\St(\Phi, S^{-1} R)\) on the pro-group \(\St^{(\infty)}(\Phi, R)\).
 The morphism \(\mathrm{st} \colon \St^{(\infty)}(\Phi, R) \to \GG^{(\infty)}(\Phi, R)\) is equivariant with respect to this action.
 This action also satisfies the equality \[\up{x_\alpha(u)}{x_\alpha(a^{(\infty)})} = x_\alpha(a^{(\infty)}).\]
\end{prop}
\begin{proof} 
 It can be checked directly that the root subgroup morphisms \[\{\up{x_\alpha(u)} x_\beta \colon R^{(\infty)} \to \St^{(\infty)}(\Phi\setminus\{\pm\alpha\}, R) \mid \beta \neq \pm \alpha \}\] defined above satisfy the defining relations of $\St^{(\infty)}(\Phi\setminus\{\pm \alpha\}, R)$.
 Consequently, by~\cref{rem:xpma-presentation} they give rise to an endomorphism of $\St^{(\infty)}(\Phi\setminus\{\pm\alpha\}, R)$, which we denote by $\up{x_\alpha(u)}(-)$.
 Since $\St^{(\infty)}(\Phi\setminus\{\pm\alpha\}, R)$ is isomorphic to $\St^{(\infty)}(\Phi, R)$ by~\cref{SingleRootElimination}, we obtain an endomorphism of $\St^{(\infty)}(\Phi, R)$, which we also denote by $\up{x_\alpha(u)}(-)$.
 
 It is easy to see that the mapping $u \mapsto \up{x_\alpha(u)}(-)$, in fact, specifies a group homomorphism $S^{-1}R \to \Aut(\St^{(\infty)}(\Phi, R))$. 
 
 The next step of the proof is to verify that the constructed action satisfies the Steinberg relations~\eqref{R2}--\eqref{R4} defining the group $\St(\Phi, S^{-1}R)$.
 Let $R_{\alpha, \beta}$ be one of these relations involving the roots $\alpha$ and $\beta$ in the left-hand side. Denote by $\Phi_0$ the rank $2$ root subsystem spanned by $\alpha$ and $\beta$. Let $\gamma \in \Phi\setminus \Phi_0$ be a root. We claim that a direct computation involving \cref{root-action}, the pro-analogues of~\eqref{R2}--\eqref{R4} and~\eqref{eq:m-mult} shows that the conjugation by the left and right side of $R_{\alpha, \beta}$ transform $x_\gamma$ to the same morphism $R^{(\infty)} \to \St^{(\infty)}(\Phi, R)$.
 Indeed, during each consecutive application of the conjugation action from~\cref{root-action} no root subgroup morphism $x_\delta$, $\delta \in \Phi_0$ may appear, which guarantees that the computation does not ``stuck''. Thus, by~\cref{DoubleRootElimination} we obtain that the automorphisms of conjugation by the left and right side of $R_{\alpha,\beta}$ are, in fact, the same automorphism of $\St^{(\infty)}(\Phi, R)$.
 
 The equivariance of the morphism \(\mathrm{st}\) is clear from the definitions. Finally, if $\alpha$ decomposes as $\beta + \gamma$ for some roots \(\beta, \gamma \in \Phi\) having the same length as $\alpha$ then \begin{align*}
  \up{x_\alpha(u)}{x_\alpha(N_{\beta, \gamma} b^{(\infty)} c^{(\infty)})} &= [\up{x_\alpha(u)}{x_\beta(b^{(\infty)})}, \up{x_\alpha(u)}{x_\gamma(c^{(\infty)})}]\\
  &= [x_\beta(b^{(\infty)}), x_\gamma(c^{(\infty)})] = x_\alpha(N_{\beta, \gamma} b^{(\infty)} c^{(\infty)}),
 \end{align*}
 which implies the last claim.
\end{proof}

\begin{theorem}\label{ChevalleyLocalAction}
 Let \(R\) be a ring, \(M \trianglelefteq R\) be a maximal ideal and \(\Phi\) be a root system of rank \(\geq 3\) different from \(\rB_\ell\) and \(\rC_\ell\). Set \(S = R \setminus M\). Then the action of $\St(\Phi, R_M)$ defined in~\cref{SteinbergLocalAction} gives rise to an action of the group \(\GG_{sc}(\Phi, R_M)\) on \(\St^{(\infty)}(\Phi, R)\). The morphism \(\mathrm{st} \colon \St^{(\infty)}(\Phi, R) \to \GG^{(\infty)}(\Phi, R)\) is \(\GG_{sc}(\Phi, R_M)\)-equivariant.
\end{theorem}
\begin{proof}
 Recall that for \(a, b \in R_M^\times\) and \(\alpha \in \Phi\) one can define the following elements of $\St(\Phi, R_M)$: 
  \begin{align*} w_\alpha(a) & =  x_\alpha(a) \cdot x_{-\alpha}(-a^{-1}) \cdot x_\alpha(a), \\
                 h_\alpha(a) & =  w_\alpha(a) \cdot w_\alpha(1)^{-1}, \\
                 \{ a,\-b \}_\alpha & = h_\alpha(ab) \cdot h_\alpha^{-1}(a) \cdot h_\alpha^{-1}(b). \end{align*}
 Since $R_M$ is local, the group $\GG_{sc}(\Phi, R_M)$ coincides with its elementary subgroup $\E(\Phi, R)$.
 Consquently, by~\cite[Theorem~2.13]{Ste73} the group \(\GG_{sc}(\Phi, R_M)\) is the quotient of \(\St(\Phi, R_M)\) by the relations $\{a,\-b\}_\alpha = 1$ for \(a, b \in R_M^\times\) and some fixed long root $\alpha\in\Phi$. Thus, it remains to check that the Steinberg symbols $\{a,\-b\}_\alpha$ act trivially on \(\St^{(\infty)}(\Phi, R)\), which, in turn, follows from the relations
 \begin{equation}\label{eq:h-conj} \up{h_\alpha(a)}x_\beta(b^{(\infty)}) = x_\beta(a^{\langle \beta, \alpha \rangle}b^{(\infty)}),\ \beta\neq\pm\alpha. \end{equation}
 
 Now let \(\beta \in \Phi\) be a root linearly independent with \(\alpha\).
 Direct computation using~\cref{root-action} shows that
 \[\up{h_\alpha(a)}{x_\beta(b^{(\infty)})} = \prod_{\substack{i\alpha + j\beta \in \Phi\\ j > 0}} x_{i\alpha + j\beta}(P_{i, j}(a) \cdot {b^{(\infty)}}^j)\]
 for some Laurent polynomials \(P_{i, j}(t) \in \mathbb Z[t, t^{-1}]\) depending only on \(\alpha\) and \(\beta\) and the chosen order of factors. Since in the Steinberg group \(\St(\Phi, \mathbb Z[t, t^{-1}])\) we have a similar identity
 \[\up{h_\alpha(t)}{x_\beta(1)} = \prod_{\substack{i\alpha + j\beta \in \Phi\\ j > 0}} x_{i\alpha + j\beta}(P_{i, j}(t)) = x_{\beta}(t^{\langle \beta,\-\alpha \rangle}),\]
 we conclude by~\cref{rem:uni-rad} that \(P_{i, j}(t) = 0\) with the sole exception of \(P_{0, 1}(t) = t^{(\beta, \alpha)}\). Thus, the proof of~\eqref{eq:h-conj} is complete.
\end{proof}

\section{Steinberg crossed module}
In this section we prove our main result, namely that Steinberg group \(\St(\Phi, R)\) is a crossed module over \(\GG(\Phi, R)\). For the rest of this section $R$ is an arbitrary commutative ring and $M$ is a maximal ideal of $R$.
As before, \(\Phi\) is a root system of rank \(\geq 3\) different from \(\rB_\ell\) and \(\rC_\ell\).

Let $S = R\setminus M$ be the multiplicative system associated to a maximal ideal $M \trianglelefteq R$.
Notice that by~\cref{ChevalleyLocalAction} the group $\GG_{sc}(\Phi, R)$ acts on both $\St^{(\infty)}(\Phi, R)$ and $\GG^{(\infty)}(\Phi, R)$ by conjugation and this action is preserved by the morphism $\mathrm{st}$.
We denote by \[\pi_R \colon R^{(\infty)} \to R,\ \pi_{\St} \colon \St^{(\infty)}(\Phi, R) \to \St(\Phi, R)\text{ and } \pi_{\GG} \colon \GG^{(\infty)}(\Phi, R) \to \GG(\Phi, R).\] the canonical pro-group morphisms. Notice that the action of $h\in \GG_{sc}(\Phi, R)$ is preserved by $\pi_{\GG}$, i.\,e. $\up{h}\pi_{\GG}(g^{(\infty)}) = \pi_{\GG}(\up{h} {g^{(\infty)}})$.
Similarly, the conjugation action of $h\in \St(\Phi, R)$ on $\St^{(\infty)}(\Phi, R)$ is preserved by $\pi_{\St}$, i.\,e. $\up{h}\pi_{\St}(g^{(\infty)}) = \pi_{\St}(\up{h}{g^{(\infty)}})$.
Notice also that $\pi_R x_\alpha = x_\alpha \pi_{\St}$ and $\pi_{\GG} \mathrm{st} = \mathrm{st}\pi_{\St}$.

\begin{lemma}\label{CentralityK2}
 The subgroup \(\mathrm K_2(\Phi, R) = \Ker(\mathrm{st} \colon \St(\Phi, R) \to \GG(\Phi, R))\) is contained in the center of \(\St(\Phi, R)\).
\end{lemma}
\begin{proof}
 Let $g$ be an element of $\mathrm K_2(\Phi, R)$ and $\alpha \in \Phi$ be a root. Consider the ideal
 \[I = \{a \in R \mid \up g {x_\alpha(ra)} = x_\alpha(ra) \text{ for all } r \in R\}.\]
 We need to show that \(I = R\). Let $M \trianglelefteq R$ be a maximal ideal.
 Since the element \(g\) acts trivially on the pro-group \(\St^{(\infty)}(\Phi, R)\) associated with $S = R \setminus M$,
 we obtain the following equality of morphisms $R^{(\infty)} \to \St(\Phi, R)$:
 \begin{multline*}
  \up g {x_\alpha(\pi_R(a^{(\infty)}))}
  = \up g{\pi_{\St}(x_\alpha(a^{(\infty)}))}
  = \pi_{\St}(\up g{x_\alpha(a^{(\infty)})})= \\
  = \pi_{\St}(x_\alpha(a^{(\infty)}))
  = x_\alpha(\pi_R(a^{(\infty)})),
 \end{multline*}
 which implies that \(I \not \subseteq M\).
\end{proof}

%The next result is actually well-known. % !!!!!!!!! Add references !!!!!!!!!!!

\begin{lemma}\label{Normality}
 The subgroup \(\mathrm E(\Phi, R) = \mathrm{Im}(\mathrm{st} \colon \St(\Phi, R) \to \GG_{sc}(\Phi, R))\) is normal in \(\GG_{sc}(\Phi, R)\).
\end{lemma}
\begin{proof}
 Let $g$ be an element of $\GG_{sc}(\Phi, R)\) and \(\alpha \in \Phi\) be a root. Consider the ideal
 \[I = \{a \in R \mid \up g{t_\alpha(ra)} \in \mathrm E(\Phi, R)\text{ for all }r\in R\}.\]
 Again, we need to show that \(I = R\). Let \(M \trianglelefteq R\) be a maximal ideal. 
 Since \(g\) acts on the pro-groups \(\St^{(\infty)}(\Phi, R)\) and $\GG^{(\infty)}(\Phi, R)$ associated with the subset $S = R \setminus M$ and 
 this action is preserved by $\mathrm{st}$, we obtain the following equality of morphisms $R^{(\infty)} \to \GG_{sc}(\Phi, R)$:
 \[
  \up g{t_\alpha(\pi_R(a^{(\infty)}))}
  = \up g{\pi_{\GG}(\mathrm{st}(x_\alpha(a^{(\infty)})))}
  = \pi_{\GG}(\mathrm{st}(\up g{x_\alpha(a^{(\infty)})}))
  = \mathrm{st}(\pi_{\St}(\up g{x_\alpha(a^{(\infty)})})),
 \]
 which implies that \(I \not \subseteq M\).
\end{proof}

Let $N$ be a group acting on itself by left conjugation.
A group homomorphism $\varphi\colon M \to N$ is called a {\it crossed module} if one can define the action of the group $N$ on $M$ in such a way that that $\varphi$ preserves the action of $N$ and, moreover, the identity ${}^{\varphi(m)}\!m' = m m' m^{-1}$, called {\it Peiffer identity}, holds for all $m, m' \in M$.

\begin{theorem}\label{SteinbergCrossedModule}
 The homomorphism \(\mathrm{st} \colon \St(\Phi, R) \to \GG_{sc}(\Phi, R)\) can be turned into a crossed module in a unique way.
\end{theorem}
\begin{proof}  
 Notice that under our assumptions the group $\E(\Phi, R)$ is perfect, therefore by~\cite[Lemma~1.1]{St71} for every $g\in \GG_{sc}(\Phi, R)$ there may exist at most one endomorphism $\up g (-)$ of $\St(\Phi, R)$ satisfying 
 \begin{equation} \label{eq:scm-2}\up{g}{\mathrm{st}(h)} = \mathrm{st} (\up g h)\text{ for all }h \in \St(\Phi, R).  \end{equation}
 Thus, to construct an action of $\GG_{sc}(\Phi, R)$ on $\St(\Phi, R)$ it suffices to construct an endomorphism 
  \(\up g{(-)} \colon \St(\Phi, R) \to \St(\Phi, R)\) satisfying~\eqref{eq:scm-2}.
 Also, this action would automatically satisfy Peiffer identity.
 
 Notice that by~\cref{CentralityK2} we already know that $\mathrm K_2(\Phi, R)$ is a central subgroup of $\St(\Phi, R)$.
 Let $\alpha$ be a root of $\Phi$. Since \(\mathrm E(\Phi, R) \trianglelefteq \GG_{sc}(\Phi, R)\) by~\cref{Normality}, the set
 $Y_\alpha(a) = \mathrm{st}^{-1}\bigl(g{t_\alpha(a)} g^{-1}\bigr)$ is nonempty for all \(a \in R\). 
 Moreover, $Y_\alpha(a)$ is a coset of the subgroup \(\mathrm K_2(\Phi, R)\) and \(Y_\alpha(a + a') = Y_\alpha(a) Y_\alpha(a')\).

 First of all, let us show that \([Y_\alpha(a), Y_\beta(b)] = 1\) provided \(\alpha + \beta \notin \Phi \cup \{0\}\). 
 Let \(\alpha, \beta\) be roots as above, $a$ be an element of $R$ and $h$ be an element of $Y_\alpha(a)\).
 Set $I = \{b \in R \mid [h, Y_\beta(bR)] = 1\}$ and let \(M \trianglelefteq R\) be a maximal ideal. Since
 \[[h, \pi_{\St}(\up g {x_\beta(b^{(\infty)})})] = \pi_{\St}(\up{g t_\alpha(a)} {x_\beta(-b^{(\infty)})}) \pi_{\St}(\up g {x_\beta(-b^{(\infty)})}) = 1,\]
 we obtain that \(I \not \subseteq M\) and, consequently, that \(I = R\), which proves the assertion.

 Now let $\alpha$ be a root of $\Phi$. By our assumptions on $\Phi$ there exist roots \(\beta, \gamma \in \Phi\) of the same length such that \(\alpha = \beta + \gamma\). Denote by \(y_\alpha(a)\) the only element of the set \([Y_\beta(N_{\beta, \gamma}), Y_\gamma(a)]\). 
 We define the endomorphism $\up g (-)$ on the generators of $\St(\Phi, R)$ by $\up g {x_\alpha(a)} = y_\alpha(a)$. 
 Clearly, \(y_\alpha(a)\) satisfy~\eqref{R1}. Since $y_\alpha(a) \in Y_\alpha(a)$ we also obtain that $y_\alpha(a)$ satisfy relations~\eqref{R2}.
 
 It remains to check that \(y_\alpha(a)\) satisfy the Steinberg relations \eqref{R3} and \eqref{R4}.
 Let \(M \trianglelefteq R\) be a maximal ideal. First of all, notice that
 \begin{multline} \label{eq:scm1}
  y_\alpha(\pi_R(a^{(\infty)})) = [Y_\beta(N_{\beta, \gamma}), \pi_{\St}(\up g{x_\gamma(a^{(\infty)})})] =\\
  = \pi_{\St}\bigl(\up{g t_\beta(N_{\beta, \gamma})}{x_\gamma(a^{(\infty)})}\, \up g{x_\gamma(-a^{(\infty)})}\bigr) = \pi_{\St}(\up g{x_\alpha(a^{(\infty)})}).
 \end{multline}
 
 Now let $a$ be an element of $R$ and \(\alpha, \beta\) be roots of $\Phi$ such that \(\alpha + \beta, 2\alpha + \beta \in \Phi\). 
 Consider the ideal
 \begin{align*}
 J = \{b \in R &\mid [y_\alpha(a), y_\beta(br)] = \\
 &= y_{\alpha + \beta}(N_{\alpha, \beta} abr)
 y_{2\alpha + \beta}(N_{\alpha, \beta}^{2,1} a^2 br) \text{ for all } r \in R\}.
 \end{align*}
 From~\eqref{eq:scm1} we obtain that
 \begin{align*}
 [y_\alpha(a), y_\beta(\pi_R(b^{(\infty)}))] &= [y_\alpha(a), \pi_{\St}(\up g{x_\beta(b^{(\infty)})})]\\ 
 &= \pi_{\St}\bigl(\up{g t_\alpha(a)}{x_\beta(b^{(\infty)})}\, \up g{x_\beta(-b^{(\infty)})}\bigr)\\
 &= \pi_{\St}\bigl(\up g{x_{\alpha + \beta}(N_{\alpha, \beta} a b^{(\infty)})}\, \up g{x_{2\alpha + \beta}(N_{\alpha, \beta}^{2,1} a^2 b^{(\infty)})}\bigr)\\
 &= y_{\alpha + \beta}(N_{\alpha, \beta} a \pi_R(b^{(\infty)})) y_{2\alpha + \beta}(N_{\alpha, \beta}^{2,1} a^2 \pi_R(b^{(\infty)})).
 \end{align*}
 It follows that \(J \not \subseteq M\), i.e. \(J = R\). The verification of~\eqref{R3} is similar but easier.   
 
 It is clear that the constructed endomorphism satisfies~\eqref{eq:scm-2}. \end{proof}
\printbibliography
\end{document}
